---
title: "Effect of dynamic mask speed on suppression of a moving stimulus: Two Mask Direction Switch modes"
author: "Egor Ananyev"
date: '2016-04-28'
output:
    html_document:
        toc: true
---

<style type="text/css">
body, td{
  font-family: Cambria;
}
code.r{
  font-family: Inconsolata;
}
</style>

# Preparing the data

## Loading the packages and data
```{r set-options, message=F}
options(width=108)
out=F
# The list of subjects, the order of conditions, and the thresholds are derived from Subjects.xlsx
library(xlsx)
library(ggplot2)
library(plyr)
library(matrixStats)
library(splines)
library(lme4)
library(lmerTest)
library(reshape)
# Neat functions:
db <- '/home/egor/Dropbox/' # on Linux
db <- '~/Dropbox/' # on Mac
db <- '/Users/Egor/Dropbox/' # Windows
source(paste(db, 'Prog/R/myFunctions/blackTheme.R', sep=''))
source(paste(db, 'Prog/R/myFunctions/pvalfn.R', sep=''))
# Read in the Excel worksheet:
dataDir <- paste(db, 'Projects/dm/data/', sep='')
condDir <- paste(dataDir,'bcfs7/', sep='')
subjList <- read.xlsx(file=paste(dataDir, 'Subjects.xlsx', sep=''), sheetName='bcfs6&7', 
                      colIndex=c(1:3), header=T)
subjList$Subj<- as.factor(subjList$Subj)
condList <- c('s1')
# dropSubjs <- c(2) # X[ ! X$Variable1 %in% c(11,12), ]
nConds <- 13
nc <- nConds-1 # the number of conditions without the blank
shortRT <- .5
outlFac <- 2.5 # outlier factor
# Gathering the directories from the data directory:
allDirs <- dir(condDir)
```

## Pre-processing the data
```{r}
# Setting variables for the loop:
ds <- data.frame()
allrts <- data.frame()
aarts <- data.frame()
rtds <- data.frame()
curSubj <- 7 #temp
curCond <- 1 #temp
for(curSubj in 1:length(subjList$Subj)){ #going through all dirs
    for(curCond in 1:length(condList)){
        print(paste('curSubj =', as.character(curSubj), 'curCond =', 
                    as.character(curCond)))
        grepPattern <- paste('dm7_p-', subjList$Subj[curSubj], '_dom-', 
                             subjList$DomEye[curSubj],
                             '_', condList[curCond], '_t0_', sep='')
        subjDir <- allDirs[grep(grepPattern, allDirs)]
        # With this directory, extracting data:
        subjDataFN <- paste(condDir, subjDir, '/', subjDir, '_trials.tsv', sep='')
        if(file.exists(subjDataFN)){
            ss <- read.table(subjDataFN, sep='\t', nrows=nConds, header=T)
            sumss <- ss[,1:27]
            # Inserting subject ID and subject threshold
            sumss$SubjID <- subjList$Subj[curSubj]
            sumss$subjThresh <- subjList$subjThresh[curSubj]
            # I can't take RT_mean, because it doesn't exclude zeros
            # Need to get the RTs on my own, and since the nTrials might
            # differ...
            nTrials <- ss$n[1]
            rts <- ss[,30:(29+nTrials)]
            if(curCond==1){
                allrts <- rts
            }else{
                allrts <- cbind(rts,allrts)
            }
            print(paste('Processed file',subjDataFN))
        }else{
            print(paste('File does not exist:',subjDataFN))
        }
    }
    # Counting and removing RTs<shortRT and non-responses
    sumss$cnt_RTshort <- c(rowSums(allrts[1:nc,]<shortRT),0) 
    sumss$cnt_RTna <- rowSums(allrts==0)
    # Handling non-responses in two different ways: either equating them to 3s (max RT) or to NA
    rt3 <- allrts
    rt3[rt3==0] <- 3 #maximum rt
    sumss$RT3_mean <- 0 # c(rowMeans(rt3[1:nc,],na.rm=T),0)
    sumss$RT3_mean <- c(rowMeans(rt3[1:nc,],na.rm=T),0)
    sumss$RT3_norm <- c(sumss$RT3_mean[1:nc]/mean(sumss$RT3_mean[1:nc],na.rm=T),0)
    sumss$RT3_norm <- 0
    sumss$RT3_norm[1:(nc/2)] <- sumss$RT3_mean[1:(nc/2)]/mean(sumss$RT3_mean[1:(nc/2)],na.rm=T)
    sumss$RT3_norm[(nc/2+1):nConds] <- c(sumss$RT3_mean[(nc/2+1):nc]/mean(sumss$RT3_mean[(nc/2+1):nc],
                                                                          na.rm=T),0)
    # RTs with exclusions as NA:
    rtna <- allrts
    rtna[rtna==0] <- NA
    rtna[rtna<shortRT] <- NA
    # Dealing with the outliers:
    sumss$RTna_mean <- c(rowMeans(rtna[1:nc,],na.rm=T),0)
    sumss$RTna_median <- c(rowMedians(as.matrix(rtna[1:nc,]),na.rm=T),0)
    sumss$RTna_sd <- c(apply(rtna[1:nc,],1,sd,na.rm=T),0)
    sumss$RTna_outlLow <- rowSums(rtna<(sumss$RTna_mean-outlFac*sumss$RTna_sd), na.rm=T)
    sumss$RTna_outlHigh <- rowSums(rtna>(sumss$RTna_mean+outlFac*sumss$RTna_sd), na.rm=T)
    rtna[rtna<(sumss$RTna_mean-outlFac*sumss$RTna_sd)] <- NA
    rtna[rtna>(sumss$RTna_mean+outlFac*sumss$RTna_sd)] <- NA
    sumss$RTna_mean <- c(rowMeans(rtna[1:nc,],na.rm=T),0)
    sumss$RTna_sd <- c(apply(rtna[1:nc,],1,sd,na.rm=T),0)
    sumss$RTna_norm <- c(sumss$RTna_mean[1:nc]/mean(sumss$RTna_mean[1:nc],na.rm=T),0)
    sumss$RTna_norm[1:(nc/2)] <- sumss$RTna_mean[1:(nc/2)]/mean(sumss$RTna_mean[1:(nc/2)],na.rm=T)
    sumss$RTna_norm[(nc/2+1):nConds] <- c(sumss$RTna_mean[(nc/2+1):nc]/
                                          mean(sumss$RTna_mean[(nc/2+1):nc], na.rm=T),0)
    # Filling up aarts only after rtna has been cleaned up
    if(curSubj==1){
        aarts <- cbind(sumss,rtna)
    }else{
        aarts <- rbind(aarts,cbind(sumss,rtna))
    }
    # Binding the summary statistics with the empty data frame
    ds <- rbind(ds, sumss)
    rtds <- rbind(rtds,aarts)
}
# ds$maskSpeed <- as.factor(ds$maskSpeed)
# ds$maskDirSwitch <- as.factor(ds$maskDirSwitch)
shams <- ds[ds$targSpeed==0,]
ds <- ds[ds$targSpeed!=0,]

# Excluding the participant with ~3rd of blanks as false alarms:
#ds <- ds[ds$SubjID!=7,]
#subjList <- subjList[subjList$Subj!=7,]
#ds <- ds[ ! ds$SubjID %in% c(7,9,12), ]
#subjList <- subjList[ ! subjList$Subj %in% c(7,9,12), ]

# Splitting subjects into high- and low-threshold pools:
subjTl <- subjList$Subj[subjList$subjThresh<1]
subjTh <- subjList$Subj[subjList$subjThresh>1]
dsTl <- ds[ds$SubjID %in% subjTl,]
dsTh <- ds[ds$SubjID %in% subjTh,]
```

## Preparing the tall data sets
```{r}
# Preparing the data set...
# Creating character strings for naming the trials:
rtss <- rtds
trialColNames <- paste('t',as.character(c(1:24)),sep='')
colnames(rtss)[(length(rtss)-23):(length(rtss))] <- trialColNames
# Melting the data set to have a trial per row:
md <- melt(rtss, id=c('SubjID','subjThresh','maskDirSwitch','maskSpeed','targSpeed'),
           measure.vars=trialColNames)
mdBlanks <- md[md$targSpeed==0,]
md <- md[md$targSpeed!=0,] # deleting blank trials
rownames(md)=NULL
# Renaming the variables for trial and RT:
md <- rename(md,c('variable'='trial','value'='RT'))
# Renaming the trial variables to trial number:
# nSubj <- 8
# md$trial <- rep(c(1:24),each=48*nSubj)
md$trial <- as.numeric(substr(as.character(md$trial),2,3))
head(md)
# Trimming mdBlanks
#mdBlanks <- rename(mdBlanks,c('variable'='trial','value'='RT'))
#rownames(mdBlanks)=NULL
#mdBlanks$trial <- as.numeric(substr(as.character(mdBlanks$trial),2,3))
```

# Quality checks

## Individual thresholds
```{r, fig.height=3, fig.width=4}
# Rearranging based on the threshold value:
subjList <- arrange(subjList,subjThresh)
subjList$altSubj <- as.character(c(101:(100+nrow(subjList))))
# Line plots for non-broken trials:
ggplot(subjList, aes(x=Subj, y=subjThresh, fill=Subj)) + geom_bar(stat='identity') + 
    theme_bw() + labs(y='Threshold Time') + 
    theme(legend.position='none', axis.title.x=element_blank(), axis.text.x = element_blank())
if(out){pdf("dm7thresh.pdf", width=4, height=3)}
ggplot(subjList, aes(x=altSubj, y=subjThresh)) + geom_bar(stat='identity') + 
    theme_bw() + labs(y='Threshold Time') + 
    theme(legend.position='none', axis.text.x = element_blank()) + labs(x='Participant')
if(out){dev.off()}
```

## False alarms
```{r, fig.height=3, fig.width=4}
shams$fas <- shams$n - shams$cnt_RTna #multiplying by 3 bc there were 3 sessions
shamSum <- ddply(shams, .(SubjID), summarise, fasTot=sum(fas), nTot=sum(n))
shamSum$fasP <- shamSum$fas / shamSum$n
print(shamSum)
p <- ggplot(shamSum, aes(x=SubjID, y=fasP)) + geom_bar(stat='identity') + 
    theme_bw() + labs(y='False Alarms', x='Participant') + #ylim(0,1) +
    scale_y_continuous(limits = c(0,1), breaks=seq(0,1,.25)) + 
    theme(legend.position='none', axis.text.x = element_blank(), panel.border = element_blank(),
          axis.text=element_text(size=8), axis.title=element_text(size=9), 
          panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank())
plot(p)
```


## Non-breaking trials
```{r, fig.height=3, fig.width=5}
# Line plots for non-broken trials

## Switching mask directions
ggplot(ds[ds$maskDirSwitch==1,], aes(x=maskSpeed, y=cnt_RTna/24, group=SubjID, colour=SubjID)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='Number of non-breaking trials') + theme_bw()
## Non-switching mask
ggplot(ds[ds$maskDirSwitch==0,], aes(x=maskSpeed, y=cnt_RTna/24, group=SubjID, colour=SubjID)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='Number of non-breaking trials') + theme_bw()
ss = ddply(ds, .(maskSpeed,maskDirSwitch), summarise, `Mean non-breaking trials`=mean(cnt_RTna/24))
## Mean non-breaking trials
ggplot(ss, aes(x=maskSpeed, y=`Mean non-breaking trials`, colour=maskDirSwitch, group=maskDirSwitch)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Mask Direction Switch') + theme_bw()
```

## RT SDs
```{r, fig.height=3, fig.width=5}
## Switching mask
ggplot(ds[ds$maskDirSwitch==1,], aes(x=maskSpeed, y=RTna_sd, group=SubjID, colour=SubjID)) + 
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='RT standard deviation') + theme_bw()
## Non-switching mask
ggplot(ds[ds$maskDirSwitch==0,], aes(x=maskSpeed, y=RTna_sd, group=SubjID, colour=SubjID)) + 
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='RT standard deviation') + theme_bw()
```

## RT Outliers (low)
```{r, fig.height=3, fig.width=4}
## Switching mask:
ggplot(ds[ds$maskDirSwitch==1,], aes(x=SubjID, y=RTna_outlLow, fill=SubjID)) + 
    geom_bar(stat='identity') + labs(x='Subject ID',y='Low outlier count') +
    theme(legend.position='none') + theme_bw()
## Non-switching mask:
ggplot(ds[ds$maskDirSwitch==0,], aes(x=SubjID, y=RTna_outlLow, fill=SubjID)) + 
    geom_bar(stat='identity') + labs(x='Subject ID',y='Low outlier count') +
    theme(legend.position='none') + theme_bw()
```

## RT Outliers (high)
```{r, fig.height=3, fig.width=4}
## Switching mask:
ggplot(ds[ds$maskDirSwitch==1,], aes(x=SubjID, y=RTna_outlHigh, fill=SubjID)) + 
    geom_bar(stat='identity') + labs(x='Subject ID',y='High outlier count') +
    theme(legend.position='none') + theme_bw()
# Non-switching mask:
ggplot(ds[ds$maskDirSwitch==0,], aes(x=SubjID, y=RTna_outlHigh, fill=SubjID)) + 
    geom_bar(stat='identity') + labs(x='Subject ID',y='High outlier count') +
    theme(legend.position='none') + theme_bw()
```

# Reaction times

## Raw RTs separately for two mask switching modes
```{r, fig.height=3, fig.width=5}
# Line plots of raw RTs per subject
ggplot(ds[ds$maskDirSwitch==1,], aes(x=maskSpeed, y=RTna_mean, group=SubjID, colour=SubjID)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='Mean RT') + theme_bw()
ggplot(ds[ds$maskDirSwitch==0,], aes(x=maskSpeed, y=RTna_mean, group=SubjID, colour=SubjID)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='Mean RT') + theme_bw()
```

## Normalized RTs for two mask switching modes
```{r, fig.height=3, fig.width=5}
# Line plots of normalized RTs
ggplot(ds[ds$maskDirSwitch==1,], aes(x=maskSpeed, y=RTna_norm, group=SubjID, colour=SubjID)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='Normalized RT') + theme_bw()
ggplot(ds[ds$maskDirSwitch==0,], aes(x=maskSpeed, y=RTna_norm, group=SubjID, colour=SubjID)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='Normalized RT') + theme_bw()
```

# Summary plots

## Box plots

### Raw
```{r, fig.height=3, fig.width=5}
ggplot(ds, aes(x=factor(maskSpeed), y=RTna_mean, colour=factor(maskDirSwitch))) + geom_boxplot() + 
    labs(x='Mask Speed', colour='Mask Direction Switch', y='Mean RT') + theme_bw()
```

### Normalized
```{r, fig.height=3, fig.width=5}
ggplot(ds, aes(x=factor(maskSpeed), y=RTna_norm, colour=factor(maskDirSwitch))) + geom_boxplot() + 
    labs(x='Mask Speed', colour='Mask Direction Switch', y='Mean RT') + theme_bw()
```

## Smoothed on raw

### Normalized data set
```{r}
# Compiling a data set containing two normalized values
# Normalizing by subject
mds <- ddply(md, .(SubjID), summarise, subjMean=mean(RT, na.rm=T))
mdn <- merge(md,mds,by='SubjID')
# Normalizing by motion pattern
mdc <- ddply(md, .(SubjID, maskDirSwitch), summarise, condMean=mean(RT, na.rm=T))
mdn <- merge(mdn,mdc,by=c('SubjID','maskDirSwitch'))
# Computing the normalized RTs
mdn$subjNormRT <- mdn$RT / mdn$subjMean
mdn$subjNormRTcond <- mdn$RT / mdn$condMean # TEMP
# Computing the subject means for dot-plotting:
subjMeans <- ddply(mdn, .(SubjID, maskDirSwitch, maskSpeed), summarise, 
                   subjNormMean=mean(subjNormRT, na.rm=T),
                   subjRTMean=mean(RT, na.rm=T),
                   subjNormMeanCond=mean(subjNormRT, na.rm=T))
```

### Linear fit (publication format)
```{r, fig.height=4, fig.width=7}
mdns <- ddply(mdn, .(SubjID, subjThresh, maskDirSwitch, maskSpeed), summarise,
                meanSubjST = mean(subjNormRT, na.rm=T))
mdnsum <- ddply(mdns, .(maskDirSwitch, maskSpeed), summarise,
                meanCondST = mean(meanSubjST), 
                seCondST = sd(meanSubjST) / sqrt(length(SubjID)))
dodge <- position_dodge(width=.0)
alpha <- .6
p <- ggplot(mdnsum, aes(x=maskSpeed, y=meanCondST, colour=factor(maskDirSwitch), 
                        group=factor(maskDirSwitch), 
                        ymax=meanCondST+seCondST,  ymin=meanCondST-seCondST)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_x_continuous(breaks=unique(ss$maskSpeed),
                       labels=as.character(unique(ss$maskSpeed))) + theme_bw() +
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), y='Normalized Suppression Time',
         colour=' Mask\n Switching') + 
    guides(colour=guide_legend(keyheight=.2, default.unit='inch')) +
    scale_color_manual(labels = c('No','Yes'), values=c('#E69F00', '#0072B2')) + 
    theme_bw() + ylim(.8,1.2) +
    theme(panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank(),
          axis.text=element_text(size=8), axis.title=element_text(size=9),
          legend.text=element_text(size=8), legend.title=element_text(size=9),
          legend.key = element_blank(), #legend.margin=unit(-.04, 'in'),
          legend.background = element_rect(fill='transparent'))
if(!out){plot(p)}else{png('dm7lin.png', width=3.5, height=2.1, units='in', res=600); plot(p); dev.off()}
```

# Linear models

## Centering the data
```{r}
# Centering some variables:
md$maskSpeed_ctr <- with(md, maskSpeed-3)
md$maskSwitch_ctr <- with(md, maskDirSwitch*2-1)
md$subjThresh_ctr <- with(md, subjThresh-mean(subjThresh))

# Preparing the data set:
md$trialN <- substr(md$trial, 2, 3)
md$trialN <- as.numeric(md$trialN)

head(md)
```

## Full linear model
```{r}
m_full <- lmer(RT~maskSwitch_ctr*maskSpeed_ctr+subjThresh_ctr+(1|SubjID),md)
pvalfn(m_full)
#write.table(pvalfn(m_full),'clipboard',sep='\t',row.names=T)
```