---
title: "Effects of matching mask/target motion pattern and speed"
author: "Egor Ananyev"
date: '2016-03-03'
output:
    html_document:
        toc: true
---

<style type="text/css">
body, td{
  font-family: Cambria;
}
code.r{
  font-family: Inconsolata;
}
</style>

# Preparing the data

## Packages and data
```{r set-options, message=F, warning=F}
options(width=108)
out=F
# The list of subjects, the order of conditions, and the thresholds are derived from Subjects.xlsx
library(xlsx)
library(ggplot2)
library(plyr)
library(matrixStats)
library(splines)
library(reshape)
library(lme4)
library(lmerTest)
# Neat functions:
db <- '/home/egor/Dropbox/' # on Linux
db <- '~/Dropbox/' # on Mac
db <- '/Users/Egor/Dropbox/' # Windows
source(paste(db, 'Prog/R/myFunctions/blackTheme.R', sep=''))
source(paste(db, 'Prog/R/myFunctions/pvalfn.R', sep=''))
# Read in the Excel worksheet:
dataDir <- paste(db, 'Projects/dm/data/', sep='')
condDir <- paste(dataDir,'bcfs1/', sep='')
subjList <- read.xlsx(file=paste(dataDir, 'Subjects.xlsx', sep=''), sheetName='bcfs1', 
                      colIndex=c(1:8), header=T)
subjList$Subj <- as.factor(subjList$Subj)
subjList$Sequence <- as.factor(subjList$Sequence)
# Some additional constants:
condList <- c('cscm','csdm','dscm','dsdm')
nConds <- 6
nc <- nConds-1 # the number of conditions without the blank
shortRT <- .5
outlFac <- 2.5 # outlier factor
# Gathering the directories from the data directory:
allDirs <- dir(condDir)
# theme for plotting:
themefy <- function(p) {
    p <- p + theme_bw() + 
         theme(panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank(),
            axis.text=element_text(size=8), axis.title=element_text(size=9),
            legend.text=element_text(size=8), legend.title=element_text(size=9),
            legend.key = element_blank(), legend.margin=unit(-.04, 'in'),
            legend.background = element_rect(fill='transparent'))
}
```

## Pre-processing the data
```{r}
# Setting variables for the loop:
ds <- data.frame()
md <- data.frame()
cbound <- data.frame()
curSubj <- 1 #temp
curCond <- 1 #temp
for(curSubj in 1:length(subjList$Subj)){ #going through all dirs
    for(curCond in 1:length(condList)){
        grepPattern <- paste('dm_bcfs-', condList[curCond], '_t0_', subjList$Subj[curSubj], sep='')
        subjDir <- allDirs[grep(grepPattern, allDirs)]
        # With this directory, extracting data:
        subjDataFN <- paste(condDir, subjDir, '/', subjDir,
                            '_trials.tsv', sep='')
        if(file.exists(subjDataFN)){
            ss <- read.table(subjDataFN, sep='\t', nrows=6, header=T)
            sumss <- ss[,1:29]
            sumss$motPat[sumss$cond=='bcfs-cscm'] <- 'Rotating Target\nRotating Mask'
            sumss$motPat[sumss$cond=='bcfs-dsdm'] <- 'Linear Target\nLinear Mask'
            sumss$motPat[sumss$cond=='bcfs-csdm'] <- 'Rotating Target\nLinear Mask'
            sumss$motPat[sumss$cond=='bcfs-dscm'] <- 'Linear Target\nRotating Mask'
            sumss$mpRotMask <- 0
            sumss$mpRotMask[sumss$cond=='bcfs-cscm' | sumss$cond=='bcfs-dscm'] <- 1
            sumss$mpRotTarg <- 0
            sumss$mpRotTarg[sumss$cond=='bcfs-cscm' | sumss$cond=='bcfs-csdm'] <- 1
            sumss$mpMatch <- 0
            sumss$mpMatch[sumss$cond=='bcfs-cscm' | sumss$cond=='bcfs-dsdm'] <- 1
            # Inserting subject ID
            sumss$SubjID <- subjList$Subj[curSubj]
            sumss$subjThresh <- mean(as.numeric(subjList[curSubj, 
                                                         c('Thresh1', 'Thresh2', 'Thresh3')]), 
                                     na.rm=T)
            # I can't take RT_mean, because it doesn't exclude zeros
            # Need to get the RTs on my own, and since the nTrials might
            # differ...
            nTrials <- ss$n[1]
            rts <- ss[,30:(29+nTrials)]
            rtna <- rts
            rtna[rtna==0] <- NA
            # Counting and removing RTs<shortRT and non-responses
            sumss$cnt_RTshort <- c(rowSums(rts[1:nc,]<shortRT),0) 
            sumss$cnt_RTna <- rowSums(rts==0)
            sumss$RT0 <- rowSums(is.na(rtna))
            sumss$RTna_mean <- c(rowMeans(rtna[1:nc,],na.rm=T),0)
            sumss$RTna_median <- c(rowMedians(as.matrix(rtna[1:nc,]),na.rm=T),0)
            sumss$RTna_sd <- c(apply(rtna[1:nc,],1,sd,na.rm=T),0)
            sumss$RTna_outlLow <- rowSums(rtna<(sumss$RTna_mean-outlFac*sumss$RTna_sd), na.rm=T)
            sumss$RTna_outlHigh <- rowSums(rtna>(sumss$RTna_mean+outlFac*sumss$RTna_sd), na.rm=T)
            rtna[rtna<(sumss$RTna_mean-outlFac*sumss$RTna_sd)] <- NA
            rtna[rtna>(sumss$RTna_mean+outlFac*sumss$RTna_sd)] <- NA
            sumss$RTna_mean <- c(rowMeans(rtna[1:nc,],na.rm=T),0)
            sumss$RTna_sd <- c(apply(rtna[1:nc,],1,sd,na.rm=T),0)
            sumss$RTna_norm <- c(sumss$RTna_mean[1:nc]/mean(sumss$RTna_mean[1:nc],na.rm=T),0)
            # Binding the summary statistics with the empty data frame
            ds <- rbind(ds, sumss)
            # Gathering RTs:
            cbound <- cbind(sumss,rtna)
            # Renaming the trial columns for easy handling later: 
            trialColNames <- paste('t',as.character(c(1:nTrials)),sep='')
            colnames(cbound)[(length(cbound)-nTrials+1):(length(cbound))] <- trialColNames
            # Melting the data set to have a trial per row:
            melted <- melt(cbound, id=c('SubjID', 'subjThresh', 'motPat', 'maskSpeed','targSpeed',
                                        'mpRotMask', 'mpRotTarg', 'mpMatch'),
                       measure.vars=trialColNames)
            # Renaming the variables for trial and RT:
            melted <- rename(melted,c('variable'='trial','value'='RT'))
            if(curCond==1 & curSubj==1){
                md <- melted
            }else{
                md <- rbind(md, melted)
            }
            print(paste('Processed file',subjDataFN))
        }else{
            print(paste('File does not exist:',subjDataFN))
        }
    }
}
ds$Condition <- as.factor(substr(ds$cond, 6, 9))
shams <- ds[ds$targSpeed==0,]
ds <- ds[ds$targSpeed>0,]
mdBlanks <- md[md$targSpeed==0,]
md <- md[md$targSpeed!=0,] # deleting blank trials
rownames(md)=NULL
```

# Quality control

## Individual thresholds
```{r, fig.height=3, fig.width=4}
# Calculating the subject means for the four thresholds:
subjList$subjThresh <- rowMeans(subjList[,4:7], na.rm=F)
# Excluding subjects with missing runs:
subjList <- subjList[!is.na(subjList$subjThresh),]
# Rearranging based on the threshold value:
subjList <- arrange(subjList,subjThresh)
subjList$altSubj <- as.character(c(101:(100+nrow(subjList))))
# Line plots for non-broken trials:
p <- ggplot(subjList, aes(x=altSubj, y=subjThresh)) + geom_bar(stat='identity') + 
    theme_bw() + labs(y='Threshold Time', x='Participant') + ylim(0,2) +
    theme(legend.position='none', axis.text.x = element_blank(), panel.border = element_blank(),
          axis.text=element_text(size=8), axis.title=element_text(size=9))
plot(p)
if(!out){plot(p)}else{png('dm1thresh.png', width=3.5, height=2.1, units='in', res=600); plot(p); dev.off()}
summary(subjList$subjThresh)
sd(subjList$subjThresh) # standard deviation
sum(subjList$subjThresh<1) # subjects with thresholds less than 1
sum(subjList$subjThresh>1) # subjects with thresholds greater than 1
```

## False alarms
```{r, fig.height=2.1, fig.width=3.5}
shams$fas <- shams$n - shams$RT0
shamSum <- ddply(shams, .(SubjID), summarise, fasTot=sum(fas), nTot=sum(n))
shamSum$fasP <- shamSum$fas / shamSum$n
print(shamSum)
p <- ggplot(shamSum, aes(x=SubjID, y=fasP)) + geom_bar(stat='identity') + 
    theme_bw() + labs(y='False Alarms', x='Participant') + #ylim(0,1) +
    scale_y_continuous(limits = c(0,1), breaks=seq(0,1,.25))
p <- themefy(p)
plot(p)
```

# Visualization

## Preparing the normalized data set
```{r}
# Compiling a data set containing two normalized values
# Normalizing by subject
mds <- ddply(md, .(SubjID), summarise, subjMean=mean(RT, na.rm=T))
mdn <- merge(md,mds,by='SubjID')
# Normalizing by motion pattern
mdc <- ddply(md, .(SubjID, motPat), summarise, condMean=mean(RT, na.rm=T))
mdn <- merge(mdn,mdc,by=c('SubjID','motPat'))
# Computing the normalized RTs
mdn$subjNormRT <- mdn$RT / mdn$subjMean
mdn$condNormRT <- mdn$RT/mdn$condMean
head(mdn)
```

For this, we need a new data set that contains the summary values for normalized suppression times. First, we compute the averages of normalized RTs for every subject and condition. Then we take the average across subjects to derive a condition mean.

```{r}
mdns <- ddply(mdn, .(SubjID, subjThresh, motPat, maskSpeed), summarise,
                meanSubjST = mean(subjNormRT, na.rm=T))
mdnsum <- ddply(mdns, .(motPat, maskSpeed), summarise,
                meanCondST = mean(meanSubjST),
                seCondST = sd(meanSubjST) / sqrt(length(SubjID)))
mdnsum_lt <- ddply(mdns[mdns$subjThresh<median(mdns$subjThresh),], .(motPat, maskSpeed), summarise,
                meanCondST = mean(meanSubjST),
                seCondST = sd(meanSubjST) / sqrt(length(SubjID)))
mdnsum_ht <- ddply(mdns[mdns$subjThresh>median(mdns$subjThresh),], .(motPat, maskSpeed), summarise,
                meanCondST = mean(meanSubjST),
                seCondST = sd(meanSubjST) / sqrt(length(SubjID)))
```

## Line plots
```{r, fig.height=2.1, fig.width=3.5}
dodge <- position_dodge(width=0)
alpha <- .6
p <- ggplot(mdnsum, aes(x=maskSpeed, y=meanCondST, colour=motPat, group=motPat,
                        ymin=meanCondST-seCondST, ymax=meanCondST+seCondST)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_x_continuous(breaks=unique(ss$maskSpeed)) + 
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), 
         y='Normalized Suppression Time',
         colour='   Motion Pattern') + ylim(.7,1.3) +
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
if(!out){plot(p)}else{png('dm1lin.png', width=3.5, height=2.1, units='in', res=600); plot(p); dev.off()}
```

## Non-breaking trials
```{r, fig.height=2.1, fig.width=3.5}
# computing mean and SD of subj means:
mdnsNb <- ddply(ds, .(SubjID, subjThresh, motPat, maskSpeed), summarise,
                meanSubjNb = mean(cnt_RTna/24, na.rm=T))
mdnsumNb <- ddply(mdnsNb, .(motPat, maskSpeed), summarise,
                meanCondNb = mean(meanSubjNb),
                seCondNb = sd(meanSubjNb) / sqrt(length(SubjID)))
# plot
p <- ggplot(mdnsumNb, aes(x=maskSpeed, y=meanCondNb, colour=motPat, group=motPat,
                          ymin=meanCondNb-seCondNb, ymax=meanCondNb+seCondNb)) +  
    geom_line(alpha=alpha) + geom_point(alpha=alpha) + 
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) + ylim(0,.2) +
    scale_x_continuous(breaks=unique(ss$maskSpeed)) + 
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), 
         y='Proportion Non-Broken Trials',
         colour='   Motion Pattern') +
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
if(!out){plot(p)}else{png('dm1nb.png', width=3.5, height=2.1, units='in', res=600); plot(p); dev.off()}
```

<!--
## Expected patterns

### FSS for pattern and speed
```{r, fig.height=2.1, fig.width=3.5}
expData = mdnsum
expData$seCondST <- 0.08
expData[expData['motPat']=='Linear Target\nLinear Mask', 'meanCondST'] <- 
    c(.85,.98,1.03,.97,.84)
expData[expData['motPat']=='Rotating Target\nRotating Mask', 'meanCondST'] <- 
    c(.86,.99,1.04,.98,.85)
expData[expData['motPat']=='Rotating Target\nLinear Mask', 'meanCondST'] <- 
    c(.65,.76,.81,.78,.62)
expData[expData['motPat']=='Linear Target\nRotating Mask', 'meanCondST'] <- 
    c(.66,.77,.82,.79,.63)
expData$meanCondST <- expData$meanCondST + .1
p <- ggplot(expData, aes(x=maskSpeed, y=meanCondST, colour=motPat, group=motPat)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    #geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_x_continuous(breaks=unique(ss$maskSpeed)) + theme_bw() +
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), y='Normalized Suppression Time',
         colour='   Motion Pattern') + 
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
# if(!out){plot(p)}else{png('dm1linPred1.png', width=3.5, height=2.1, units='in', res=600); plot(p); dev.off()}
```

### FSS only for pattern
```{r, fig.height=2.1, fig.width=3.5}
expData = mdnsum
expData$seCondST <- 0.08
expData[expData['motPat']=='Linear Target\nLinear Mask', 'meanCondST'] <- 
    c(.85,.95,1.01,1.06,1.08)
expData[expData['motPat']=='Rotating Target\nRotating Mask', 'meanCondST'] <- 
    c(.86,.96,1.02,1.07,1.09)
expData[expData['motPat']=='Rotating Target\nLinear Mask', 'meanCondST'] <- 
    c(.65,.75,.83,.88,.90)
expData[expData['motPat']=='Linear Target\nRotating Mask', 'meanCondST'] <- 
    c(.64,.74,.82,.87,.89)
expData$meanCondST <- expData$meanCondST + .1
p <- ggplot(expData, aes(x=maskSpeed, y=meanCondST, colour=motPat, group=motPat)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    #geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_x_continuous(breaks=unique(ss$maskSpeed)) + theme_bw() +
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), y='Normalized Suppression Time',
         colour='   Motion Pattern') + 
    guides(colour=guide_legend(keyheight=.3, default.unit='inch')) +
    theme(panel.grid.minor.x=element_blank(), panel.grid.minor.y=element_blank(),
          axis.text=element_text(size=8), axis.title=element_text(size=9),
          legend.text=element_text(size=8), legend.title=element_text(size=9),
          legend.key = element_blank(), legend.margin=unit(-.04, 'in'),
          legend.background = element_rect(fill='transparent'))
# if(!out){plot(p)}else{png('dm1linPred2.png', width=3.5, height=2.1, units='in', res=600); plot(p); dev.off()}
```

### Salience-driven
```{r, fig.height=2.1, fig.width=3.5}
expData = mdnsum
expData$seCondST <- 0.08
expData[expData['motPat']=='Linear Target\nLinear Mask', 'meanCondST'] <- 
    c(.85,.92,1.01,1.04,1.06)
expData[expData['motPat']=='Rotating Target\nRotating Mask', 'meanCondST'] <- 
    c(.86,.93,1.02,1.05,1.07)
expData[expData['motPat']=='Rotating Target\nLinear Mask', 'meanCondST'] <- 
    c(.87,.94,1.03,1.06,1.08)
expData[expData['motPat']=='Linear Target\nRotating Mask', 'meanCondST'] <- 
    c(.88,.95,1.04,1.07,1.09)
#expData$meanCondST <- expData$meanCondST + runif(10,.03,.06)
#expData$meanCondST <- expData$meanCondST + .1
p <- ggplot(expData, aes(x=maskSpeed, y=meanCondST, colour=motPat, group=motPat)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    #geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_x_continuous(breaks=unique(ss$maskSpeed)) + theme_bw() +
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), y='Normalized Suppression Time',
         colour='   Motion Pattern') + 
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
# if(!out){plot(p)}else{png('dm1linPred3.png', width=3.5, height=2.1, units='in', res=600); plot(p); dev.off()}
```
-->

<!--
## Line plots for Low- and High-Thresh Ps
```{r, fig.height=2.1, fig.width=3.5}
p <- ggplot(mdnsum_lt, aes(x=maskSpeed, y=meanCondST, colour=motPat, group=motPat,
                    ymax=meanCondST+seCondST,  ymin=meanCondST-seCondST)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_x_continuous(breaks=unique(ss$maskSpeed)) + theme_bw() +
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), y='Mean Suppression Time',
         colour='   Motion Pattern') + ylim(.6,1.6) +
    guides(colour=guide_legend(keyheight=.3, default.unit='inch')) +
    theme(legend.position='none')
p <- themefy(p)
if(!out){plot(p)}else{png('dm1lin2_lt.png', width=2.5, height=2, units='in', res=600); plot(p); dev.off()}
p <- ggplot(mdnsum_ht, aes(x=maskSpeed, y=meanCondST, colour=motPat, group=motPat,
                    ymax=meanCondST+seCondST,  ymin=meanCondST-seCondST)) +
    geom_point(position=dodge, size=1, alpha=alpha) +
    geom_line(position=dodge, alpha=alpha) +
    geom_linerange(position=dodge, show.legend=F, alpha=alpha) +
    scale_x_continuous(breaks=unique(ss$maskSpeed)) + theme_bw() +
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), y='Mean Suppression Time',
         colour='   Motion Pattern') + ylim(.6,1.6) +
    guides(colour=guide_legend(keyheight=.3, default.unit='inch'))
p <- themefy(p)
# if(!out){plot(p)}else{png('dm1lin2_ht.png', width=3.5, height=2, units='in', res=600); plot(p); dev.off()}
```
-->

# Linear models

## DV: Suppression times

### Preparing the data set
```{r}
# Centering some variables:
md$maskSpeed_ctr <- with(md, maskSpeed-targSpeed)
md$subjThresh_ctr <- with(md, subjThresh-mean(subjThresh))
md$mpMatch_ctr <- with(md, ((mpMatch*2) - 1) )
md$mpRotMask_ctr <- with(md, ((mpRotMask*2) - 1) )
md$mpRotTarg_ctr <- with(md, ((mpRotTarg*2) - 1) )
# Preparing the data set:
md$trialN <- substr(md$trial, 2, 3)
md$trialN <- as.numeric(md$trialN)
head(md)
```

### Linear analyses
```{r}
## Mask/target congruence
m_mpMatch <- lmer(RT~mpMatch_ctr*maskSpeed_ctr+(1|SubjID),md)
pvalfn(m_mpMatch)
#write.table(pvalfn(m_mpMatch),'clipboard',sep='\t',row.names=T)
## Target/mask types
m_mpType <- lmer(RT~mpRotMask_ctr*mpRotTarg_ctr*maskSpeed_ctr+(1|SubjID), md)
pvalfn(m_mpType)
#write.table(pvalfn(m_mpType),'clipboard',sep='\t',row.names=T)
```

<!--
### Linear models with subj thresh
```{r}
#m_mpMatch_full <- lmer(RT~trialN+mpMatch_ctr*maskSpeed_ctr*subjThresh_ctr+(1|SubjID),md)
#pvalfn(m_mpMatch_full)
# write.table(pvalfn(m_mpMatch_full),'clipboard',sep='\t',row.names=T)
#m_mpType_full <- lmer(RT~trialN+subjThresh_ctr*mpRotMask_ctr*mpRotTarg_ctr*maskSpeed_ctr+
#                              (1|SubjID), md)
#(pvalfn(m_mpType_full))
# write.table(pvalfn(m_mpType_full),'clipboard',sep='\t',row.names=T)
```
-->

### Non-linear analyses
```{r}
mdSum <- ddply(md, c('maskSpeed_ctr'), summarise, meanRT = mean(RT, na.rm=T))
head(mdSum)
fitLin <- lm(meanRT~maskSpeed_ctr, data=mdSum)
fitSquare <- nls(meanRT~a+b*maskSpeed_ctr^2, data=mdSum, start=list(a=1,b=0))
summary(fitSquare)
anova(fitLin, fitSquare)
```

<!--
### Cubic and quartic
```{r}
# fitCube <- nls(meanRT~a+b*maskSpeed_ctr^3, data=mdSum, start=list(a=1,b=0))
# summary(fitCube)
# anova(fitSquare, fitCube)
# fitQuat <- nls(RT~a+b*maskSpeed_ctr^4, data=md, start=list(a=1,b=0))
# summary(fitQuat)
# anova(fitCube, fitQuat)
```
-->

## Analysis of non-responses
 
### Preparing the data set
```{r}
# Constructing a new data set with na response count:
dsna <- ddply(md, .(SubjID, subjThresh_ctr, maskSpeed_ctr, mpRotMask_ctr, mpRotTarg_ctr, 
                    mpMatch_ctr), summarise, nNa=sum(is.na(RT)))
head(dsna)

# Characterising the new data set
dsna_sum <- ddply(dsna, .(SubjID, subjThresh_ctr), summarise, meanNa=mean(nNa), sdNa=sd(nNa),
                  countNa=sum(nNa))
dsna_sum
```

### Linear analyses
```{r}
# Targ/mask congruence
m_na_mpMatch <- lmer(nNa ~ mpMatch_ctr * maskSpeed_ctr + (1|SubjID), dsna)
pvalfn(m_na_mpMatch)
#write.table(pvalfn(m_na_mpMatch),'clipboard',sep='\t',row.names=T)
# Target/mask types
m_na_mpType <- lmer(nNa ~ mpRotMask_ctr * mpRotTarg_ctr * maskSpeed_ctr + (1|SubjID), dsna)
pvalfn(m_na_mpType)
#write.table(pvalfn(m_na_mpType),'clipboard',sep='\t',row.names=T)
```

<!--
### Linear models with subj thresh
```{r}
#m_na_mpMatch_full <- lmer(nNa ~ mpMatch_ctr * maskSpeed_ctr * subjThresh_ctr + (1|SubjID), dsna)
#pvalfn(m_na_mpMatch_full)
#m_na_mpType_full <- lmer(nNa ~ mpRotMask_ctr * mpRotTarg_ctr * maskSpeed_ctr * subjThresh_ctr + 
#                        (1|SubjID), dsna)
#pvalfn(m_na_mpType_full)
```
-->