---
title: "Effect of dynamic mask speed on suppression of a moving stimulus: Effect of limited trajectory length"
author: "Egor Ananyev"
date: '2016-04-28'
output:
    html_document:
        toc: true
---

<style type="text/css">
body, td{
  font-family: Cambria;
}
code.r{
  font-family: Inconsolata;
}
</style>

# Preparing the data

## Loading the packages and data
```{r set-options, message=F}
options(width=108)
out=F
# The list of subjects, the order of conditions, and the thresholds are derived from Subjects.xlsx
library(BayesFactor)
# Neat functions:
db <- '/home/egor/Dropbox/' # on Linux
db <- '~/Dropbox/' # on Mac
db <- '/Users/Egor/Dropbox/' # Windows
source(paste(db, 'Prog/R/myFunctions/blackTheme.R', sep=''))
source(paste(db, 'Prog/R/myFunctions/pvalfn.R', sep=''))
```

# Bayes Factor

## bcfs-1

### Mask-target match

```{r}
source(paste(db, 'Projects/dm/dm/an/subj-bcfs-1.Rmd', sep=''))
# conventional model
m_mpMatch_full <- lmer(RT~trialN+mpMatch_ctr*maskSpeed_ctr*subjThresh_ctr+(1|SubjID),md)
pvalfn(m_mpMatch_full)
# dataset:
mdNoNa <- md[!is.na(md$RT),]
# Bayes Factor on mask-target match:
regRand <- lmBF(RT ~ SubjID, data = mdNoNa, whichRandom = 'SubjID')
regPart <- lmBF(RT ~ maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regPart / regRand
regFull <- lmBF(RT ~ mpMatch_ctr + maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regFull / regRand
regPart / regFull
regFull / regPart 
# Bayes Factor on mask-target match X mask speed interaction:
regRand <- lmBF(RT ~ SubjID, data = mdNoNa, whichRandom = 'SubjID')
regNi <- lmBF(RT ~ mpMatch_ctr + maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regNi / regRand
regFull <- lmBF(RT ~ mpMatch_ctr + maskSpeed_ctr + mpMatch_ctr:maskSpeed_ctr + SubjID, 
                data=mdNoNa, whichRandom = 'SubjID')
regFull / regRand
regNi / regFull
regFull / regNi
#write.table(bf,'clipboard',sep='\t',row.names=T)
```

### Mask pattern vs target pattern of motion

```{r}
# conventional model
m_mpType_full <- lmer(RT~trialN+subjThresh_ctr*mpRotMask_ctr*mpRotTarg_ctr*maskSpeed_ctr+
                              (1|SubjID), md)
pvalfn(m_mpType_full)
# dataset:
mdNoNa <- md[!is.na(md$RT),]
# Bayes Factor on mask-target match:
regRand <- lmBF(RT ~ SubjID, data = mdNoNa, whichRandom = 'SubjID')
regPart <- lmBF(RT ~ maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regPart / regRand

# Contribution of the mask pattern of motion:
regFull <- lmBF(RT ~ mpRotMask_ctr + maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regFull / regRand
regPart / regFull
regFull / regPart 

# Contribution of the target pattern of motion
regFull <- lmBF(RT ~ mpRotTarg_ctr + maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regFull / regRand
regPart / regFull
regFull / regPart 

# Contribution of the mask X target pattern of motion interaction:
regPart <- lmBF(RT ~ mpRotTarg_ctr + mpRotMask_ctr + maskSpeed_ctr + SubjID, data=mdNoNa, 
                whichRandom = 'SubjID')
regFull <- lmBF(RT ~ mpRotTarg_ctr + mpRotMask_ctr + maskSpeed_ctr + 
                    mpRotTarg_ctr:mpRotMask_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regPart / regFull
regFull / regPart 
```

### Mask pattern effect on no-response trials

```{r}
# conventional model:
m_na_mpType <- lmer(nNa ~ mpRotMask_ctr * mpRotTarg_ctr * maskSpeed_ctr + (1|SubjID), dsna)
# Contribution of the mask pattern of motion:
regRand <- lmBF(nNa ~ SubjID, data = dsna, whichRandom = 'SubjID')
regPart <- lmBF(nNa ~ maskSpeed_ctr + SubjID, data=dsna, whichRandom = 'SubjID')
regFull <- lmBF(nNa ~ mpRotMask_ctr + maskSpeed_ctr + SubjID, data=dsna, whichRandom = 'SubjID')
regFull / regRand
regPart / regFull
regFull / regPart 
```

## bcfs-4

```{r}
source(paste(db, 'Projects/dm/dm/an/subj-bcfs-4.Rmd', sep=''))
# conventional model
m_full <- lmer(RT~targSpeed_ctr*maskSpeed_ctr*subjThresh_ctr+(1|SubjID),md)
pvalfn(m_full)
# dataset:
mdNoNa <- md[!is.na(md$RT),]
# Bayes Factor on the target speed:
regRand <- lmBF(RT ~ SubjID, data = mdNoNa, whichRandom = 'SubjID')
regPart <- lmBF(RT ~ maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regPart / regRand
regFull <- lmBF(RT ~ targSpeed_ctr + maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regFull / regRand
regPart / regFull
regFull / regPart 
# Bayes model of the mask X target speed interaction
regRand <- lmBF(RT ~ SubjID, data = mdNoNa, whichRandom = 'SubjID')
regNi <- lmBF(RT ~ targSpeed_ctr + maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regNi / regRand
regFull <- lmBF(RT ~ targSpeed_ctr + maskSpeed_ctr + targSpeed_ctr:maskSpeed_ctr + SubjID, 
                data=mdNoNa, whichRandom = 'SubjID')
regFull / regRand
regNi / regFull
regFull / regNi
#write.table(bf,'clipboard',sep='\t',row.names=T)
```

## bcfs-5

```{r}
source(paste(db, 'Projects/dm/dm/an/subj-bcfs-5.Rmd', sep=''))
# conventional model
m_full <- lmer(RT~targSpeed_ctr*maskSpeed_ctr+subjThresh_ctr+(1|SubjID),md)
pvalfn(m_full)
# dataset:
mdNoNa <- md[!is.na(md$RT),]
# target speed:
regRand <- lmBF(RT ~ SubjID, data = mdNoNa, whichRandom = 'SubjID')
regPart <- lmBF(RT ~ maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regPart / regRand
regFull <- lmBF(RT ~ targSpeed_ctr + maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regFull / regRand
regPart / regFull
regFull / regPart 
# interaction
regRand <- lmBF(RT ~ SubjID, data = mdNoNa, whichRandom = 'SubjID')
regNi <- lmBF(RT ~ targSpeed_ctr + maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regNi / regRand
regFull <- lmBF(RT ~ targSpeed_ctr + maskSpeed_ctr + targSpeed_ctr:maskSpeed_ctr + SubjID, 
                data=mdNoNa, whichRandom = 'SubjID')
regFull / regRand
regNi / regFull
regFull / regNi
#write.table(bf,'clipboard',sep='\t',row.names=T)
```

Neither model is preferred when compared to the random intercept-only model or to each other. I.e., the interaction term does not seem to contribute.

## bcfs-6

```{r}
source(paste(db, 'Projects/dm/dm/an/subj-bcfs-6.Rmd', sep=''))
# conventional model
m_full <- lmer(RT~targSpeed_ctr*maskSpeed_ctr+subjThresh_ctr+(1|SubjID),md)
pvalfn(m_full)
# dataset:
mdNoNa <- md[!is.na(md$RT),]
# target speed:
regRand <- lmBF(RT ~ SubjID, data = mdNoNa, whichRandom = 'SubjID')
regPart <- lmBF(RT ~ maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regPart / regRand
regFull <- lmBF(RT ~ targSpeed_ctr + maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regFull / regRand
regPart / regFull
regFull / regPart 
# interaction:
mdNoNa <- md[!is.na(md$RT),]
regRand <- lmBF(RT ~ SubjID, data = mdNoNa, whichRandom = 'SubjID')
regNi <- lmBF(RT ~ targSpeed_ctr + maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regNi / regRand
regFull <- lmBF(RT ~ targSpeed_ctr + maskSpeed_ctr + targSpeed_ctr:maskSpeed_ctr + SubjID, 
                data=mdNoNa, whichRandom = 'SubjID')
regFull / regRand
regNi / regFull
regFull / regNi
```

### Target X mask speed interaction on no-response trials

```{r}
# conventional model:
m_na <- lmer(nNa ~ targSpeed_ctr * maskSpeed_ctr + (1|SubjID), dsna)
# Contribution of the mask pattern of motion:
regRand <- lmBF(nNa ~ SubjID, data = dsna, whichRandom = 'SubjID')
regPart <- lmBF(nNa ~ targSpeed_ctr + maskSpeed_ctr + SubjID, data=dsna, whichRandom = 'SubjID')
regFull <- lmBF(nNa ~ targSpeed_ctr * maskSpeed_ctr + SubjID, data=dsna, whichRandom = 'SubjID')
regFull / regRand
regPart / regFull
regFull / regPart 
```

## bcfs-7

```{r}
source(paste(db, 'Projects/dm/dm/an/subj-bcfs-7.Rmd', sep=''))
# conventional model
m_full <- lmer(RT~maskSwitch_ctr*maskSpeed_ctr+subjThresh_ctr+(1|SubjID),md)
pvalfn(m_full)
# dataset:
mdNoNa <- md[!is.na(md$RT),]
# target speed:
regRand <- lmBF(RT ~ SubjID, data = mdNoNa, whichRandom = 'SubjID')
regPart <- lmBF(RT ~ maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regPart / regRand
regFull <- lmBF(RT ~ maskSwitch_ctr + maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regFull / regRand
regPart / regFull
regFull / regPart 
# interaction:
regRand <- lmBF(RT ~ SubjID, data = mdNoNa, whichRandom = 'SubjID')
regNi <- lmBF(RT ~ maskSwitch_ctr + maskSpeed_ctr + SubjID, data=mdNoNa, whichRandom = 'SubjID')
regNi / regRand
regFull <- lmBF(RT ~ maskSwitch_ctr + maskSpeed_ctr + maskSwitch_ctr:maskSpeed_ctr + SubjID, 
                data=mdNoNa, whichRandom = 'SubjID')
regFull / regRand
regNi / regFull
regFull / regNi
```