---
title: "Frequency Analysis of Stimuli"
author: "Egor Ananyev"
date: "6/16/2017"
output:
    html_document:
        toc: true
---

<style type="text/css">
body, td{
  font-family: Cambria;
}
code.r{
  font-family: Inconsolata;
}
</style>

```{r set-options, message=F}
# options(width=108)
out=F
```

# Data prep

## Read in the data
```{r}
library(png)
library(spectral)
library(ggplot2)
db <- '/Users/Egor/Dropbox/' # Windows & Mac
stimDir <- paste(db, 'Projects/dm/stimuli/targ1-v1_mask1-v1/', sep='')
```

## Setting variables
```{r}
# RGB+Y grayscale values
y <- .66
g <- .58
r <- g*165/255
b <- r*160/255
# screen resolution and stimulus dimensions
res <- c(1680,1050) # resolution
offs <- c(313,307) # offsets along x and y (169,165)
stimSz <- 276 # 151
dims <- c(stimSz+1, stimSz+1)
```

# SF

## Loading the last frame
```{r}
# read in the last frame:
fileList <- dir(stimDir, '*.png')
nFrames <- length(fileList)
frame <- readPNG(paste(stimDir, fileList[nFrames], sep=''))
```

## Preparing the target image
```{r}
# plotting:
#plot(1:2, type='n')
cutTarg <- function(frame, res.=res, offs.=offs, stimSz.=stimSz){
    xEdges <- c(res.[1]/2-offs.[1]-round(stimSz./2),
                res.[1]/2-offs.[1]+round(stimSz./2))
    yEdges <- c(res.[2]/2-offs.[2]-round(stimSz./2),
                res.[2]/2-offs.[2]+round(stimSz./2))
    targIm <- frame[yEdges[1]:yEdges[2],xEdges[1]:xEdges[2],]
    targIm[which(targIm==1)] <- 0 # removing the fixation dot
    targIm <- targIm[,,1] + targIm[,,2] + targIm[,,3]
    targIm <- targIm/3
    # targIm <- targIm/max(targIm)
    return(targIm)
}
targImS <- cutTarg(frame) # single target image
# identifying the fixation coordinates:
## checking for symmetry; the two numbers should be the same:
# fix <- which(targIm==1)
# dimSz <- length(targIm[,1,1]) # length of the first two dimensions
# (dimSz*dimSz/2)-fix[1]
# fix[length(fix)]-(dimSz*dimSz/2)
# plotting the image:
plot(-2.5:2.5, -2.5:2.5, type='n', xlab='', ylab='')
rasterImage(targImS, -2.5, -2.5, 2.5, 2.5)
```

## SF analysis of target
```{r}
fftOut <- spec.fft(targImS)
plot(fftOut)
```

## Mask image
```{r}
cutMask <- function(frame, res.=res, offs.=offs, stimSz.=stimSz){
    xEdgesMask <- c(res.[1]/2+offs.[1]+2-round(stimSz./2),
                    res.[1]/2+offs.[1]+2+round(stimSz./2))
    yEdgesMask <- c(res.[2]/2-offs.[2]-round(stimSz./2),
                    res.[2]/2-offs.[2]+round(stimSz./2))
    maskIm <- frame[yEdgesMask[1]:yEdgesMask[2],xEdgesMask[1]:xEdgesMask[2],]
    return(maskIm)
}
recolor <- function(maskIm, y.=y, r.=r, g.=g, b.=b){
    maskIm[(maskIm[,,1]+maskIm[,,2])+maskIm[,,3]==3] <- 0 # discarding the fixation dot
    maskIm[(maskIm[,,1]+maskIm[,,2])==2] <- y.
    maskIm[maskIm[,,1]==1] <- r.
    maskIm[maskIm[,,2]==1] <- g.
    maskIm[maskIm[,,3]==1] <- b.
    maskIm <- maskIm[,,1] + maskIm[,,2] + maskIm[,,3]
    maskIm <- maskIm/max(maskIm)
    return(maskIm)
}
```

## Trimming the mask image
```{r}
maskImS <- cutMask(frame) # single mask image
maskImS <- recolor(maskImS)
plot(-2.5:2.5, -2.5:2.5, type='n', xlab='', ylab='')
rasterImage(maskImS, -2.5, -2.5, 2.5, 2.5)
```

## SF analysis of the mask
```{r}
fftOutMask <- spec.fft(maskImS)
plot(fftOutMask)
```

# TF

## Loading the sequence of frames
```{r}
stimDir <- paste(db, 'Projects/dm/stimuli/targs/', sep='')
fileList <- dir(stimDir, '*.png')
```

### Targ
```{r}
#frames <- array(NA, dim=c(dim(frame),nFrames))
targIm <- array(NA, dim=c(dims,nFrames,3)) # 3 targ speeds
targVs <- c(1,3,5)
for(curV in 1:3){
    # print(paste('curV', curV))
    fileSubList <- grep(paste('targ1-v', as.character(targVs[curV]),sep=''), 
                        fileList, value=T)
    for(frameN in 1:nFrames){
        # print(paste('frameN', frameN))
        #frames[,,,frameN] <- readPNG(paste(stimDir, dir(stimDir)[frameN], sep=''))
        frame <- readPNG(paste(stimDir, fileSubList[frameN], sep=''))
        targIm[,,frameN,curV] <- cutTarg(frame)
        # targIm <- cutTarg(frame)
        # writePNG(targIm, paste(stimDir, 'targ/', tools::file_path_sans_ext(fileList[frameN]), 
        #                        '_targ.png', sep=''))
    }
}
```

### Mask
```{r}
#frames <- array(NA, dim=c(dim(frame),nFrames))
maskIm <- array(NA, dim=c(dims,nFrames,3))
for(curV in c(.3,1,2,3,5,8)){
    for(frameN in 1:nFrames){
        #frames[,,,frameN] <- readPNG(paste(stimDir, dir(stimDir)[frameN], sep=''))
        frame <- readPNG(paste(stimDir, fileList[frameN], sep=''))
        maskImTemp <- cutMask(frame)
        maskIm[,,frameN,curV] <- recolor(maskImTemp)
        # maskIm <- cutMask(frame)
        # maskIm <- recolor(maskIm)
        # writePNG(maskIm, paste(stimDir, 'mask/', tools::file_path_sans_ext(fileList[frameN]),
        #                        '_mask.png', sep=''))
    }
}
```

## Pixelwise on target

```{r}
xy <- expand.grid(1:dims[1],1:dims[2]) # x & y coordinate combinations
freqs <- spectrum(targIm[1,1,,1],plot=F)$freq # frequencies
```

<!--
### Raster images on high/low frequencies
```{r}
medFreq <- .25 # frameN/60/8
targSpecLo <- array(NA, dim=dims) # for 2d rendering
targSpecHi <- array(NA, dim=dims)
#TEMP: a single, example, pixel:
# pixInd <- which(targImS>.5, arr.ind=T)[350,] # x=104 y=89
for(x in 1:dims[1]){
    for(y in 1:dims[2]){
        targSpec <- spectrum(targIm[x,y,], plot=F)
        targSpecLo[x,y] <- sum(targSpec$spec[targSpec$freq<medFreq])
        targSpecHi[x,y] <- sum(targSpec$spec[targSpec$freq>=medFreq])
    }
}
targSpecDf <- data.frame(targSpecs, colnames=c('x','y',char(targSpec$freq)))
plot(-2.5:2.5, -2.5:2.5, type='n', xlab='', ylab='')
rasterImage(targSpecLo/max(targSpecLo), -2.5, -2.5, 2.5, 2.5)
plot(-2.5:2.5, -2.5:2.5, type='n', xlab='', ylab='')
rasterImage(targSpecHi/max(targSpecHi), -2.5, -2.5, 2.5, 2.5)
```
--->

### Average power across all pixels
```{r}
targSpecs <- t(apply(xy, 1, function(x) spectrum(targIm[x[1],x[2],],plot=F)$spec))
targSpecDf <- data.frame(freq=freqs, power=colMeans(targSpecs))
ggplot(targSpecDf, aes(x=freq, y=power)) + geom_line() + theme_bw()
```

## Pixelwise on mask

<!--
### Raster images on high/low frequencies
```{r}
maskSpecLo <- array(NA, dim=dims)
maskSpecHi <- array(NA, dim=dims)
ptm <- proc.time()
for(x in 1:dims[1]){
    for(y in 1:dims[2]){
        maskSpec <- spectrum(maskIm[x,y,], plot=F)
        maskSpecLo[x,y] <- sum(maskSpec$spec[maskSpec$freq<medFreq])
        maskSpecHi[x,y] <- sum(maskSpec$spec[maskSpec$freq>=medFreq])
    }
}
proc.time()-ptm
plot(-2.5:2.5, -2.5:2.5, type='n', xlab='', ylab='')
rasterImage(maskSpecLo/max(maskSpecLo), -2.5, -2.5, 2.5, 2.5)
plot(-2.5:2.5, -2.5:2.5, type='n', xlab='', ylab='')
rasterImage(maskSpecHi/max(maskSpecHi), -2.5, -2.5, 2.5, 2.5)
```
--->

### Average power across all pixels
```{r, fig.width=5, fig.height=3}
maskSpecs <- t(apply(xy, 1, function(x) spectrum(maskIm[x[1],x[2],],plot=F)$spec))
maskSpecDf <- data.frame(freq=freqs, power=colMeans(maskSpecs))
ggplot(maskSpecDf, aes(x=freq, y=power)) + geom_line() + theme_bw()
```
