---
title: "Effects of matching mask/target motion pattern and speed"
author: "Egor Ananyev"
date: '2016-03-03'
output:
    html_document:
        toc: true
---

<style type="text/css">
body, td{
  font-family: Cambria;
}
code.r{
  font-family: Inconsolata;
}
</style>

# Preparing the data

## Loading the packages and data
```{r set-options, message=F, warning=F}
options(width=108)
out=F
# The list of subjects, the order of conditions, and the thresholds are derived from Subjects.xlsx
library(xlsx)
library(ggplot2)
library(plyr)
library(matrixStats)
library(splines)
library(reshape)
library(lme4)
library(lmerTest)
# Neat functions:
db <- '/home/egor/Dropbox/' # on Linux
db <- '~/Dropbox/' # on Mac
db <- '/Users/Egor/Dropbox/' # Windows
source(paste(db, 'Prog/R/myFunctions/blackTheme.R', sep=''))
source(paste(db, 'Prog/R/myFunctions/pvalfn.R', sep=''))
# Read in the Excel worksheet:
dataDir <- paste(db, 'Projects/supr-eff/data_bcfs1/', sep='')
subjList <- read.xlsx(file=paste(dataDir,'Subjects.xlsx',sep=''), 1, colIndex=c(1:8), header=T)
subjList$Subj<- as.factor(subjList$Subj)
subjList$Sequence <- as.factor(subjList$Sequence)
condList <- c('cscm','csdm','dscm','dsdm')
# Some additional constants:
nConds <- 6
nc <- nConds-1 # the number of conditions without the blank
shortRT <- .5
outlFac <- 2.5 # outlier factor
# Gathering the directories from the data directory:
allDirs <- dir(dataDir)
```

## Pre-processing the data
```{r}
# Setting variables for the loop:
ds <- data.frame()
md <- data.frame()
cbound <- data.frame()
curSubj <- 1 #temp
curCond <- 1 #temp
for(curSubj in 1:length(subjList$Subj)){ #going through all dirs
    for(curCond in 1:length(condList)){
        grepPattern <- paste('dm_bcfs-', condList[curCond], '_t0_', subjList$Subj[curSubj], sep='')
        subjDir <- allDirs[grep(grepPattern, allDirs)]
        # With this directory, extracting data:
        subjDataFN <- paste(dataDir, subjDir, '/', subjDir,
                            '_trials.tsv', sep='')
        if(file.exists(subjDataFN)){
            ss <- read.table(subjDataFN, sep='\t', nrows=6, header=T)
            sumss <- ss[,1:29]
            sumss$motPat[sumss$cond=='bcfs-cscm'] <- '\nRotating Target\nRotating Mask\n '
            sumss$motPat[sumss$cond=='bcfs-dsdm'] <- '\nLinear Target\nLinear Mask\n '
            sumss$motPat[sumss$cond=='bcfs-csdm'] <- '\nRotating Target\nLinear Mask\n '
            sumss$motPat[sumss$cond=='bcfs-dscm'] <- '\nLinear Target\nRotating Mask\n '
            sumss$mpRotMask <- 0
            sumss$mpRotMask[sumss$cond=='bcfs-cscm' | sumss$cond=='bcfs-dscm'] <- 1
            sumss$mpRotTarg <- 0
            sumss$mpRotTarg[sumss$cond=='bcfs-cscm' | sumss$cond=='bcfs-csdm'] <- 1
            sumss$mpMatch <- 0
            sumss$mpMatch[sumss$cond=='bcfs-cscm' | sumss$cond=='bcfs-dsdm'] <- 1
            # Inserting subject ID
            sumss$SubjID <- subjList$Subj[curSubj]
            sumss$subjThresh <- mean(as.numeric(subjList[curSubj, 
                                                         c('Thresh1', 'Thresh2', 'Thresh3')]), 
                                     na.rm=T)
            # I can't take RT_mean, because it doesn't exclude zeros
            # Need to get the RTs on my own, and since the nTrials might
            # differ...
            nTrials <- ss$n[1]
            rts <- ss[,30:(29+nTrials)]
            rtna <- rts
            rtna[rtna==0] <- NA
            sumss$RTna_mean <- c(rowMeans(rtna[1:nc,],na.rm=T),0)
            sumss$RTna_median <- c(rowMedians(as.matrix(rtna[1:nc,]),na.rm=T),0)
            sumss$RTna_sd <- c(apply(rtna[1:nc,],1,sd,na.rm=T),0)
            sumss$RTna_outlLow <- rowSums(rtna<(sumss$RTna_mean-outlFac*sumss$RTna_sd), na.rm=T)
            sumss$RTna_outlHigh <- rowSums(rtna>(sumss$RTna_mean+outlFac*sumss$RTna_sd), na.rm=T)
            rtna[rtna<(sumss$RTna_mean-outlFac*sumss$RTna_sd)] <- NA
            rtna[rtna>(sumss$RTna_mean+outlFac*sumss$RTna_sd)] <- NA
            sumss$RTna_mean <- c(rowMeans(rtna[1:nc,],na.rm=T),0)
            sumss$RTna_sd <- c(apply(rtna[1:nc,],1,sd,na.rm=T),0)
            sumss$RTna_norm <- c(sumss$RTna_mean[1:nc]/mean(sumss$RTna_mean[1:nc],na.rm=T),0)
            # Binding the summary statistics with the empty data frame
            ds <- rbind(ds, sumss)
            # Gathering RTs:
            cbound <- cbind(sumss,rtna)
            # Renaming the trial columns for easy handling later: 
            trialColNames <- paste('t',as.character(c(1:nTrials)),sep='')
            colnames(cbound)[(length(cbound)-nTrials+1):(length(cbound))] <- trialColNames
            # Melting the data set to have a trial per row:
            melted <- melt(cbound, id=c('SubjID', 'subjThresh', 'motPat', 'maskSpeed','targSpeed',
                                        'mpRotMask', 'mpRotTarg', 'mpMatch'),
                       measure.vars=trialColNames)
            # Renaming the variables for trial and RT:
            melted <- rename(melted,c('variable'='trial','value'='RT'))
            if(curCond==1 & curSubj==1){
                md <- melted
            }else{
                md <- rbind(md, melted)
            }
            print(paste('Processed file',subjDataFN))
        }else{
            print(paste('File does not exist:',subjDataFN))
        }
    }
}
ds$Condition <- as.factor(substr(ds$cond, 6, 9))
ds <- ds[ds$targSpeed>0,]
mdBlanks <- md[md$targSpeed==0,]
md <- md[md$targSpeed!=0,] # deleting blank trials
rownames(md)=NULL
```

# Quality control

## Individual thresholds
```{r, fig.height=3, fig.width=4}
# Calculating the subject means for the four thresholds:
subjList$subjThresh <- rowMeans(subjList[,4:7], na.rm=F)
# Excluding subjects with missing runs:
subjList <- subjList[!is.na(subjList$subjThresh),]
# Rearranging based on the threshold value:
subjList <- arrange(subjList,subjThresh)
subjList$altSubj <- as.character(c(101:(100+nrow(subjList))))
# Line plots for non-broken trials:
if(out){pdf("expt1thresh.pdf", width=4, height=3)}
ggplot(subjList, aes(x=altSubj, y=subjThresh)) + geom_bar(stat='identity') + 
    theme_bw() + labs(y='Threshold Value') + 
    theme(legend.position='none', axis.title.x=element_blank(), axis.text.x = element_blank())
if(out){dev.off()}
summary(subjList$subjThresh)
sd(subjList$subjThresh) # standard deviation
sum(subjList$subjThresh<1) # subjects with thresholds less than 1
sum(subjList$subjThresh>1) # subjects with thresholds greater than 1
```
# Visualizations

## Line and Box plots

### Normalized line plot
```{r, fig.height=3, fig.width=5}
# Creating a data set with summaries per condition
ss = ddply(ds, .(maskSpeed,Condition), summarise, `Mean Normalized RT`=mean(RTna_norm))
ggplot(ss, aes(x=maskSpeed, y=`Mean Normalized RT`, colour=Condition, group=Condition)) + 
    geom_line() + geom_point() +  theme_bw()
```

### Raw box plot
```{r, fig.height=3, fig.width=7}
ggplot(ds, aes(x=factor(maskSpeed), y=RTna_mean, colour=motPat)) +  geom_boxplot() + 
    labs(x='Mask Speed', colour='Motion Pattern', y='Mean RT') + theme_bw()
```

### Normalized box plot
```{r, fig.height=3, fig.width=7}
ggplot(ds, aes(x=factor(maskSpeed), y=RTna_norm, colour=motPat)) +  geom_boxplot() + 
    labs(x='Mask Speed', colour='Motion Pattern', y='Normalized RT') + theme_bw()
```

## Smoothed on raw

### Cubic effects
```{r, fig.height=3, fig.width=7}
ggplot(md, aes(x=maskSpeed, y=RT, colour=factor(motPat), group=factor(motPat))) +  
    stat_smooth(method='lm', formula=y~ns(x,3), alpha=.1, aes(fill=factor(motPat)), 
                show.legend=F) +
    geom_point(data=ds, aes(x=maskSpeed, y=RTna_mean, colour=motPat), 
               position=position_dodge(width=.5), size=1, alpha=.5) + # square is shape=7
    labs(x='Mask Speed', y='RT', colour='Motion Pattern') + theme_bw()
```

## Smoothed on normalized

### Preparing the normalized data set
```{r}
# Compiling a data set containing two normalized values
# Normalizing by subject
mds <- ddply(md, .(SubjID), summarise, subjMean=mean(RT, na.rm=T))
mdn <- merge(md,mds,by='SubjID')
# Normalizing by motion pattern
mdc <- ddply(md, .(SubjID, motPat), summarise, condMean=mean(RT, na.rm=T))
mdn <- merge(mdn,mdc,by=c('SubjID','motPat'))
# Computing the normalized RTs
mdn$subjNormRT <- mdn$RT / mdn$subjMean
mdn$condNormRT <- mdn$RT/mdn$condMean
head(mdn)
```

### Cubic effects
```{r, fig.height=4, fig.width=7}
if(out){pdf("expt1_cubic_bw.pdf", width=5, height=3)}
ggplot(mdn, aes(x=maskSpeed, y=subjNormRT, colour=motPat, group=motPat)) +  
    stat_smooth(method='lm', formula=y~ns(x,3), alpha=.1, aes(fill=motPat), 
                show_guide=F) + 
    geom_point(data=ds, aes(x=maskSpeed, y=RTna_norm, colour=motPat), 
               position=position_dodge(width=.5), size=1, alpha=.5) + # square is shape=7
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), 
         y='Normalized RT', colour='Motion Pattern\n') + 
    scale_x_continuous(breaks=unique(mdn$maskSpeed)) + theme_bw()
if(out){dev.off()}
if(out){pdf("expt1_loess_bw.pdf", width=5, height=3)}
ggplot(mdn, aes(x=maskSpeed, y=subjNormRT, colour=motPat, group=motPat)) +  
    stat_smooth(method='loess', alpha=.1, aes(fill=motPat), show_guide=F) + 
    geom_point(data=ds, aes(x=maskSpeed, y=RTna_norm, colour=motPat), 
               position=position_dodge(width=.5), size=1, alpha=.5) + # square is shape=7
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), 
         y='Normalized RT', colour='Motion Pattern\n') + 
    scale_x_continuous(breaks=unique(mdn$maskSpeed)) + theme_bw()
if(out){dev.off()}
```

### High/Low Threshold Participants
```{r, fig.height=4, fig.width=7}
if(out){pdf("expt1_ht.pdf", width=5, height=3)}
ggplot(mdn[mdn$subjThresh>median(mdn$subjThresh),],
       aes(x=maskSpeed, y=subjNormRT, colour=motPat, group=motPat)) +  
    stat_smooth(method='lm', formula=y~ns(x,3), alpha=.15, aes(fill=motPat), 
                show.legend=F) + 
    geom_point(data=ds[ds$subjThresh>median(mdn$subjThresh),],
               aes(x=maskSpeed, y=RTna_norm, colour=motPat), 
               position=position_dodge(width=.5), alpha=.5, size=1) +
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), 
         y='Normalized RT', colour='Motion Pattern\n') + 
    scale_x_continuous(breaks=unique(mdn$maskSpeed)) + theme_bw()
if(out){dev.off()}
if(out){pdf("expt1_lt.pdf", width=5, height=3)}
ggplot(mdn[mdn$subjThresh<median(mdn$subjThresh),],
       aes(x=maskSpeed, y=subjNormRT, colour=motPat, group=motPat)) +  
    stat_smooth(method='lm', formula=y~ns(x,3), alpha=.1, aes(fill=motPat), 
                show.legend=F) + 
    geom_point(data=ds[ds$subjThresh<median(mdn$subjThresh),],
               aes(x=maskSpeed, y=RTna_norm, colour=motPat), 
               position=position_dodge(width=.5), alpha=.5, size=1) +
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), 
         y='Normalized RT', colour='Motion Pattern\n') + 
    scale_x_continuous(breaks=unique(mdn$maskSpeed)) + theme_bw()
if(out){dev.off()}
if(out){pdf("expt1_ht_loess.pdf", width=5, height=3)}
ggplot(mdn[mdn$subjThresh>median(mdn$subjThresh),],
       aes(x=maskSpeed, y=subjNormRT, colour=motPat, group=motPat)) +  
    stat_smooth(method='loess', alpha=.15, aes(fill=motPat), 
                show_guide=F) + 
    geom_point(data=ds[ds$subjThresh>median(mdn$subjThresh),],
               aes(x=maskSpeed, y=RTna_norm, colour=motPat), 
               position=position_dodge(width=.5), alpha=.5, size=1) +
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), 
         y='Normalized RT', colour='Motion Pattern\n') + 
    scale_x_continuous(breaks=unique(mdn$maskSpeed)) + theme_bw() + ylim(.7,1.4)
if(out){dev.off()}
if(out){pdf("expt1_lt_loess.pdf", width=5, height=3)}
ggplot(mdn[mdn$subjThresh<median(mdn$subjThresh),],
       aes(x=maskSpeed, y=subjNormRT, colour=motPat, group=motPat)) +  
    stat_smooth(method='loess', alpha=.1, aes(fill=motPat), 
                show_guide=F) + 
    geom_point(data=ds[ds$subjThresh<median(mdn$subjThresh),],
               aes(x=maskSpeed, y=RTna_norm, colour=motPat), 
               position=position_dodge(width=.5), alpha=.5, size=1) +
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), 
         y='Normalized RT', colour='Motion Pattern\n') + 
    scale_x_continuous(breaks=unique(mdn$maskSpeed)) + theme_bw() + ylim(.7,1.4)
if(out){dev.off()}
```

# Linear models

## Preparing the data set
```{r}
# Centering some variables:
md$maskSpeed_ctr <- with(md, maskSpeed-targSpeed)
md$subjThresh_ctr <- with(md, subjThresh-mean(subjThresh))
md$mpMatch_ctr <- with(md, ((mpMatch*2) - 1) )
md$mpRotMask_ctr <- with(md, ((mpRotMask*2) - 1) )
md$mpRotTarg_ctr <- with(md, ((mpRotTarg*2) - 1) )

# Preparing the data set:
md$trialN <- substr(md$trial, 2, 3)
md$trialN <- as.numeric(md$trialN)

head(md)
```

<!--
## Potentially helpful functions
```{r}
# r2.corr.mer <- function(m) {
#   lmfit <-  lm(model.response(model.frame(m)) ~ fitted(m))
#   summary(lmfit)$r.squared
# }
# e.g.,
# r2.corr.mer(m2_int)

# # Tukey
# Tukey_aov <- aov(RT~maskSpeed+motPat, data=md)
# TukeyHSD(Tukey_aov, 'motPat', ordered=T)
```

<!-- 
## The importance of centering the variables:
```{r}
md_temp <- md
m_temp1 <- lmer(RT~mpMatch*maskSpeed_ctr+(1|SubjID), md)
# mpMatch=[0,1]
pvalfn(m_temp1)
md_temp$mpMatch <- md$mpMatch - .5
m_temp2 <- lmer(RT~mpMatch*maskSpeed_ctr+(1|SubjID), md_temp)
# mpMatch=[-.5,.5]
pvalfn(m_temp2)
md_temp$mpMatch <- (md$mpMatch * 2) - 1
m_temp3 <- lmer(RT~mpMatch*maskSpeed_ctr+(1|SubjID), md_temp)
# mpMatch=[-1,1]
pvalfn(m_temp3)
# Introducing a centered variable:
m_temp6 <- lmer(RT~maskSpeed_ctr+(1|SubjID), md_temp)
pvalfn(m_temp6)
m_temp7 <- lmer(RT~maskSpeed_ctr+mpMatch+(1|SubjID), md_temp)
pvalfn(m_temp7)
m_temp8 <- lmer(RT~maskSpeed_ctr*mpMatch+(1|SubjID), md_temp)
pvalfn(m_temp8)
# Introducing a non-centered variable.
m_temp9 <- lmer(RT~maskSpeed_ctr+(1|SubjID), md)
pvalfn(m_temp9)
m_temp10 <- lmer(RT~maskSpeed_ctr+mpMatch+(1|SubjID), md)
pvalfn(m_temp10)
m_temp11 <- lmer(RT~maskSpeed_ctr*mpMatch+(1|SubjID), md)
pvalfn(m_temp11)
```
-->

## Mask/target congruence
```{r}
m_mpMatch_full <- lmer(RT~trialN+mpMatch_ctr*maskSpeed_ctr*subjThresh_ctr+(1|SubjID),md)
pvalfn(m_mpMatch_full)
# write.table(pvalfn(m_mpMatch_full),'clipboard',sep='\t',row.names=T)
```

## Target/mask types
```{r}
m_mpType_full <- lmer(RT~trialN+subjThresh_ctr*mpRotMask_ctr*mpRotTarg_ctr*maskSpeed_ctr+
                              (1|SubjID), md)
(pvalfn(m_mpType_full))
# write.table(pvalfn(m_mpType_full),'clipboard',sep='\t',row.names=T)
```

## Analysis of non-responses
 
```{r}
# Constructing a new data set with na response count:
dsna <- ddply(md, .(SubjID, subjThresh_ctr, maskSpeed_ctr, mpRotMask_ctr, mpRotTarg_ctr, 
                    mpMatch_ctr), summarise, nNa=sum(is.na(RT)))
head(dsna)

# Characterising the new data set
dsna_sum <- ddply(dsna, .(SubjID, subjThresh_ctr), summarise, meanNa=mean(nNa), sdNa=sd(nNa),
                  countNa=sum(nNa))
dsna_sum

# Targ/mask congruence
m_na_mpMatch <- lmer(nNa ~ mpMatch_ctr * maskSpeed_ctr * subjThresh_ctr + (1|SubjID), dsna)
pvalfn(m_na_mpMatch)

# Target/mask types
m_na_mpType <- lmer(nNa ~ mpRotMask_ctr * mpRotTarg_ctr * maskSpeed_ctr * subjThresh_ctr + 
                        (1|SubjID), dsna)
pvalfn(m_na_mpType)
```

## Non-linear analyses

```{r}
mdSum <- ddply(md, c('maskSpeed_ctr'), summarise, meanRT = mean(RT, na.rm=T))
head(mdSum)
fitLin <- lm(meanRT~maskSpeed_ctr, data=mdSum)
fitSquare <- nls(meanRT~a+b*maskSpeed_ctr^2, data=mdSum, start=list(a=1,b=0))
summary(fitSquare)
anova(fitLin, fitSquare)
# fitCube <- nls(meanRT~a+b*maskSpeed_ctr^3, data=mdSum, start=list(a=1,b=0))
# summary(fitCube)
# anova(fitSquare, fitCube)
# fitQuat <- nls(RT~a+b*maskSpeed_ctr^4, data=md, start=list(a=1,b=0))
# summary(fitQuat)
# anova(fitCube, fitQuat)
```