---
title: "Effect of dynamic mask speed on suppression of a moving stimulus: Two target speeds"
author: "Egor Ananyev"
date: '2016-04-28'
output:
    html_document:
        toc: true
---

```{r}
# The list of subjects, the order of conditions, and the thresholds are derived from Subjects.xlsx
# Read in the Excel worksheet:
library(xlsx)
library(ggplot2)
library(plyr)
library(matrixStats)
library(splines)
source('/Users/Egor/Dropbox/Prog/R/myFunctions/blackTheme.R')
source('/Users/Egor/Dropbox/Prog/R/myFunctions/pvalfn.R')
dataDir <- '/Users/Egor/Dropbox/Projects/supr-eff/data/'
subjList <- read.xlsx(file=paste(dataDir,'Subjects.xlsx',sep=''), 1, colIndex=c(1:8), header=T)
subjList$Subj<- as.factor(subjList$Subj)
condList <- c('s1','s2','s3')
# dropSubjs <- c(2) # X[ ! X$Variable1 %in% c(11,12), ]
nConds <- 13
nc <- nConds-1 # the number of conditions without the blank
shortRT <- .5
outlFac <- 2.5 # outlier factor
# Gathering the directories from the data directory:
allDirs <- dir(dataDir)
# Setting variables for the loop:
ds <- data.frame()
allrts <- data.frame()
aarts <- data.frame()
rtds <- data.frame()
curSubj <- 1 #temp
curCond <- 1 #temp
for(curSubj in 1:length(subjList$Subj)){ #going through all dirs
    for(curCond in 1:length(condList)){
        grepPattern <- paste('dm_p-', subjList$Subj[curSubj], '_dom-', subjList$DomEye[curSubj],
                             '_', condList[curCond], '_t0_', sep='')
        subjDir <- allDirs[grep(grepPattern, allDirs)]
        # With this directory, extracting data:
        subjDataFN <- paste(dataDir, subjDir, '/', subjDir, '_trials.tsv', sep='')
        if(file.exists(subjDataFN)){
            ss <- read.table(subjDataFN, sep='\t', nrows=nConds, header=T)
            sumss <- ss[,1:27]
            # Inserting subject ID and subject threshold
            sumss$SubjID <- subjList$Subj[curSubj]
            sumss$subjThresh <- subjList$subjThresh[curSubj]
            # I can't take RT_mean, because it doesn't exclude zeros
            # Need to get the RTs on my own, and since the nTrials might
            # differ...
            nTrials <- ss$n[1]
            rts <- ss[,30:(29+nTrials)]
            if(curCond==1){
                allrts <- rts
            }else{
                allrts <- cbind(rts,allrts)
            }
            print(paste('Processed file',subjDataFN))
        }else{
            print(paste('File does not exist:',subjDataFN))
        }
    }
    # Counting and removing RTs<shortRT and non-responses
    sumss$cnt_RTshort <- c(rowSums(allrts[1:nc,]<shortRT),0) 
    sumss$cnt_RTna <- rowSums(allrts==0)
    # Handling non-responses in two different ways: either equating them to 3s (max RT) or to NA
    rt3 <- allrts
    rt3[rt3==0] <- 3 #maximum rt
    sumss$RT3_mean <- 0 # c(rowMeans(rt3[1:nc,],na.rm=T),0)
    sumss$RT3_mean <- c(rowMeans(rt3[1:nc,],na.rm=T),0)
    sumss$RT3_norm <- c(sumss$RT3_mean[1:nc]/mean(sumss$RT3_mean[1:nc],na.rm=T),0)
    sumss$RT3_norm <- 0
    sumss$RT3_norm[1:(nc/2)] <- sumss$RT3_mean[1:(nc/2)]/mean(sumss$RT3_mean[1:(nc/2)],na.rm=T)
    sumss$RT3_norm[(nc/2+1):nConds] <- c(sumss$RT3_mean[(nc/2+1):nc]/mean(sumss$RT3_mean[(nc/2+1):nc],
                                                                          na.rm=T),0)
    # RTs with exclusions as NA:
    rtna <- allrts
    rtna[rtna==0] <- NA
    rtna[rtna<shortRT] <- NA
    # Dealing with the outliers:
    sumss$RTna_mean <- c(rowMeans(rtna[1:nc,],na.rm=T),0)
    sumss$RTna_median <- c(rowMedians(as.matrix(rtna[1:nc,]),na.rm=T),0)
    sumss$RTna_sd <- c(apply(rtna[1:nc,],1,sd,na.rm=T),0)
    sumss$RTna_outlLow <- rowSums(rtna<(sumss$RTna_mean-outlFac*sumss$RTna_sd), na.rm=T)
    sumss$RTna_outlHigh <- rowSums(rtna>(sumss$RTna_mean+outlFac*sumss$RTna_sd), na.rm=T)
    rtna[rtna<(sumss$RTna_mean-outlFac*sumss$RTna_sd)] <- NA
    rtna[rtna>(sumss$RTna_mean+outlFac*sumss$RTna_sd)] <- NA
    sumss$RTna_mean <- c(rowMeans(rtna[1:nc,],na.rm=T),0)
    sumss$RTna_sd <- c(apply(rtna[1:nc,],1,sd,na.rm=T),0)
    sumss$RTna_norm <- c(sumss$RTna_mean[1:nc]/mean(sumss$RTna_mean[1:nc],na.rm=T),0)
    sumss$RTna_norm[1:(nc/2)] <- sumss$RTna_mean[1:(nc/2)]/mean(sumss$RTna_mean[1:(nc/2)],na.rm=T)
    sumss$RTna_norm[(nc/2+1):nConds] <- c(sumss$RTna_mean[(nc/2+1):nc]/
                                          mean(sumss$RTna_mean[(nc/2+1):nc], na.rm=T),0)
    # Filling up aarts only after rtna has been cleaned up
    if(curSubj==1){
        aarts <- cbind(sumss,rtna)
    }else{
        aarts <- rbind(aarts,cbind(sumss,rtna))
    }
    # Binding the summary statistics with the empty data frame
    ds <- rbind(ds, sumss)
    rtds <- rbind(rtds,aarts)
}
# ds$maskSpeed <- as.factor(ds$maskSpeed)
# ds$targSpeed <- as.factor(ds$targSpeed)
ds <- ds[ds$targSpeed!=0,]

# Splitting subjects into high- and low-threshold pools:
subjTl <- subjList$Subj[subjList$subjThresh<1]
subjTh <- subjList$Subj[subjList$subjThresh>1]
dsTl <- ds[ds$SubjID %in% subjTl,]
dsTh <- ds[ds$SubjID %in% subjTh,]
```


# Quality checks

## Individual thresholds
```{r, fig.height=3, fig.width=4}
# Line plots for non-broken trials:
ggplot(subjList, aes(x=Subj, y=subjThresh, fill=Subj)) + geom_bar(stat='identity') + 
    theme(legend.position='none') + labs(x='Subject ID', y='Subject Threshold') +
    theme_black()
```

## Non-breaking trials
```{r, fig.height=3, fig.width=5}
# Line plots for non-broken trials:
ggplot(ds[ds$targSpeed==1,], aes(x=maskSpeed, y=cnt_RTna/24, group=SubjID, colour=SubjID)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='Number of non-breaking trials') + theme_black()
ggplot(ds[ds$targSpeed==5,], aes(x=maskSpeed, y=cnt_RTna/24, group=SubjID, colour=SubjID)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='Number of non-breaking trials') + theme_black()
ss = ddply(ds, .(maskSpeed,targSpeed), summarise, `Mean non-breaking trials`=mean(cnt_RTna/24))
ggplot(ss, aes(x=maskSpeed, y=`Mean non-breaking trials`, colour=targSpeed, group=targSpeed)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Target Speed') + theme_black()
```

## RT SDs
```{r, fig.height=3, fig.width=5}
ggplot(ds[ds$targSpeed==1,], aes(x=maskSpeed, y=RTna_sd, group=SubjID, colour=SubjID)) + 
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='RT standard deviation') + theme_black()
ggplot(ds[ds$targSpeed==5,], aes(x=maskSpeed, y=RTna_sd, group=SubjID, colour=SubjID)) + 
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='RT standard deviation') + theme_black()
```

## RT Outliers (low)
```{r, fig.height=3, fig.width=4}
ggplot(ds[ds$targSpeed==1,], aes(x=SubjID, y=RTna_outlLow, fill=SubjID)) + 
    geom_bar(stat='identity') + labs(x='Subject ID',y='Low outlier count') +
    theme(legend.position='none') + theme_black()
ggplot(ds[ds$targSpeed==5,], aes(x=SubjID, y=RTna_outlLow, fill=SubjID)) + 
    geom_bar(stat='identity') + labs(x='Subject ID',y='Low outlier count') +
    theme(legend.position='none') + theme_black()
```

## RT Outliers (high)
```{r, fig.height=3, fig.width=4}
ggplot(ds[ds$targSpeed==1,], aes(x=SubjID, y=RTna_outlHigh, fill=SubjID)) + 
    geom_bar(stat='identity') + labs(x='Subject ID',y='High outlier count') +
    theme(legend.position='none') + theme_black()
ggplot(ds[ds$targSpeed==5,], aes(x=SubjID, y=RTna_outlHigh, fill=SubjID)) + 
    geom_bar(stat='identity') + labs(x='Subject ID',y='High outlier count') +
    theme(legend.position='none') + theme_black()
```

# Reaction times

## Raw RTs
```{r, fig.height=3, fig.width=5}
# Line plots of raw RTs per subject
ggplot(ds[ds$targSpeed==1,], aes(x=maskSpeed, y=RTna_mean, group=SubjID, colour=SubjID)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='Mean RT') + theme_black()
ggplot(ds[ds$targSpeed==5,], aes(x=maskSpeed, y=RTna_mean, group=SubjID, colour=SubjID)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='Mean RT') + theme_black()
```

## Normalized RTs
```{r, fig.height=3, fig.width=5}
# Line plots of normalized RTs
ggplot(ds[ds$targSpeed==1,], aes(x=maskSpeed, y=RTna_norm, group=SubjID, colour=SubjID)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='Normalized RT') + theme_black()
ggplot(ds[ds$targSpeed==5,], aes(x=maskSpeed, y=RTna_norm, group=SubjID, colour=SubjID)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Subject ID',
                                      y='Normalized RT') + theme_black()
```

# Summary plots

## Box plots

### Raw
```{r, fig.height=3, fig.width=5}
ggplot(ds, aes(x=maskSpeed, y=RTna_mean, colour=targSpeed)) +  geom_boxplot() + 
    labs(x='Mask Speed', colour='Target Speed', y='Mean RT') + theme_black()
```

### Normalized
```{r, fig.height=3, fig.width=5}
ggplot(ds, aes(x=maskSpeed, y=RTna_norm, colour=targSpeed)) +  geom_boxplot() + 
    labs(x='Mask Speed', colour='Target Speed', y='Normalized RT') + theme_black()
```

### Raw low-threshold
```{r, fig.height=3, fig.width=5}
ggplot(dsTl, aes(x=maskSpeed, y=RTna_mean, colour=targSpeed)) +  geom_boxplot() + 
    labs(x='Mask Speed', colour='Target Speed', y='Mean RT') + theme_black()
```

### Normalized low-threshold
```{r, fig.height=3, fig.width=5}
ggplot(dsTl, aes(x=maskSpeed, y=RTna_norm, colour=targSpeed)) +  geom_boxplot() + 
    labs(x='Mask Speed', colour='Target Speed', y='Normalized RT') + theme_black()
```

## Line plots of summary RTs: Means

### Raw
```{r, fig.height=3, fig.width=5}
ss = ddply(ds, .(maskSpeed,targSpeed), summarise, `Mean RT`=mean(RTna_mean))
ggplot(ss, aes(x=maskSpeed, y=`Mean RT`, colour=targSpeed, group=targSpeed)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Target Speed') + theme_black()
```

### Smoothed
```{r, fig.height=3, fig.width=5}
ggplot(ds, aes(x=maskSpeed, y=RTna_mean, colour=targSpeed, group=targSpeed)) +  
    stat_smooth(method='lm', formula=y~ns(x,3), aes(fill=targSpeed)) + 
    labs(x='Mask Speed', y='Mean RT', colour='Target Speed') + theme_black()
```

### Normalized
```{r, fig.height=3, fig.width=5}
ss = ddply(ds, .(maskSpeed,targSpeed), summarise, `Mean Normalized RT`=mean(RTna_norm))
ggplot(ss, aes(x=maskSpeed, y=`Mean Normalized RT`, colour=targSpeed, group=targSpeed)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Target Speed') + theme_black()
```

## Line plots of summary RTs: Medians

### Mean of medians
```{r, fig.height=3, fig.width=5}
ss = ddply(ds, .(maskSpeed,targSpeed), summarise, `Median RT`=mean(RTna_median))
ggplot(ss, aes(x=maskSpeed, y=`Median RT`, colour=targSpeed, group=targSpeed)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Target Speed') + theme_black() 
```

### Median of medians
```{r, fig.height=3, fig.width=5}
ss = ddply(ds, .(maskSpeed,targSpeed), summarise, `Median RT`=median(RTna_median))
ggplot(ss, aes(x=maskSpeed, y=`Median RT`, colour=targSpeed, group=targSpeed)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Target Speed') + theme_black()
```

### Median of means
```{r, fig.height=3, fig.width=5}
ss = ddply(ds, .(maskSpeed,targSpeed), summarise, `Median RT`=median(RTna_mean))
ggplot(ss, aes(x=maskSpeed, y=`Median RT`, colour=targSpeed, group=targSpeed)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Target Speed') + theme_black()
```

### Median of normalized
```{r, fig.height=3, fig.width=5}
ss = ddply(ds, .(maskSpeed,targSpeed), summarise, `Median Normalized RT`=median(RTna_norm))
ggplot(ss, aes(x=maskSpeed, y=`Median Normalized RT`, colour=targSpeed, group=targSpeed)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Target Speed') + theme_black()
```


## Summary plots for low-threshold subjects

### Mean of medians
```{r, fig.height=3, fig.width=5}
ss = ddply(dsTl, .(maskSpeed,targSpeed), summarise, `Median RT`=mean(RTna_median))
ggplot(ss, aes(x=maskSpeed, y=`Median RT`, colour=targSpeed, group=targSpeed)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Target Speed') + theme_black()
```

### Median of medians
```{r, fig.height=3, fig.width=5}
ss = ddply(dsTl, .(maskSpeed,targSpeed), summarise, `Median RT`=median(RTna_median))
ggplot(ss, aes(x=maskSpeed, y=`Median RT`, colour=targSpeed, group=targSpeed)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Target Speed') + theme_black()
```

### Median of means
```{r, fig.height=3, fig.width=5}
ss = ddply(dsTl, .(maskSpeed,targSpeed), summarise, `Median RT`=median(RTna_mean))
ggplot(ss, aes(x=maskSpeed, y=`Median RT`, colour=targSpeed, group=targSpeed)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Target Speed') + theme_black()
```

### Raw
```{r, fig.height=3, fig.width=5}
ss = ddply(dsTl, .(maskSpeed,targSpeed), summarise, `Mean RT`=mean(RTna_mean))
ggplot(ss, aes(x=maskSpeed, y=`Mean RT`, colour=targSpeed, group=targSpeed)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Target Speed') + theme_black()
```

### Normalized
```{r, fig.height=3, fig.width=5}
ss = ddply(dsTl, .(maskSpeed,targSpeed), summarise, `Mean Normalized RT`=mean(RTna_norm))
ggplot(ss, aes(x=maskSpeed, y=`Mean Normalized RT`, colour=targSpeed, group=targSpeed)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Target Speed') + theme_black()
```

## Summary plots for high-threshold subjects

### Raw
```{r, fig.height=3, fig.width=5}
ss = ddply(dsTh, .(maskSpeed,targSpeed), summarise, `Mean RT`=mean(RTna_mean))
ggplot(ss, aes(x=maskSpeed, y=`Mean RT`, colour=targSpeed, group=targSpeed)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Target Speed') + theme_black()
```

### Normalized
```{r, fig.height=3, fig.width=5}
ss = ddply(dsTh, .(maskSpeed,targSpeed), summarise, `Mean Normalized RT`=mean(RTna_norm))
ggplot(ss, aes(x=maskSpeed, y=`Mean Normalized RT`, colour=targSpeed, group=targSpeed)) +  
    geom_line() + geom_point() + labs(x='Mask Speed', colour='Target Speed') + theme_black()
```

# Linear models
```{r}
# Loading libraries
library(lme4)
library(reshape)

# Preparing the data set...
# Creating character strings for naming the trials:
rtss <- rtds
trialColNames <- paste('t',as.character(c(1:24)),sep='')
colnames(rtss)[(length(rtss)-24):(length(rtss))] <- trialColNames
# Melting the data set to have a trial per row:
md <- melt(rtss, id=c('SubjID','subjThresh','targSpeed','maskSpeed'),measure.vars=trialColNames)
md <- md[md$targSpeed!=0,] # deleting blank trials
rownames(md)=NULL
# Renaming the variables for trial and RT:
md <- rename(md,c('variable'='trial','value'='RT'))
# Renaming the trial variables to trial number:
# nSubj <- 8
# md$trial <- rep(c(1:24),each=48*nSubj)
md$trial <- as.numeric(substr(as.character(md$trial),2,3))
```

## Smoothed on raw

### Cubic effects
```{r, fig.height=3, fig.width=5}
ggplot(md, aes(x=maskSpeed, y=RT, colour=factor(targSpeed), group=factor(targSpeed))) +  
    stat_smooth(method='lm', formula=y~ns(x,3)) + 
    labs(x='Mask Speed', y='RT',colour='Target Speed') + theme_black()
ggplot(md, aes(x=maskSpeed, y=RT, colour=factor(targSpeed), group=factor(targSpeed))) +  
    stat_smooth(method='lm', formula=y~ns(x,3)) + geom_point() +
    labs(x='Mask Speed', y='RT',colour='Target Speed') + theme_black()
```

### Quartic effects
```{r, fig.height=3, fig.width=5}
ggplot(md, aes(x=maskSpeed, y=RT, colour=factor(targSpeed), group=factor(targSpeed))) +  
    stat_smooth(method='lm', formula=y~ns(x,4)) + 
    labs(x='Mask Speed', y='RT',colour='Target Speed') + theme_black()
```

### Quartic effects with low-threshold participants
```{r, fig.height=3, fig.width=5}
ssTl <- md[md$SubjID %in% subjTl,]
ssTh <- md[md$SubjID %in% subjTh,]
ggplot(ssTl, aes(x=maskSpeed, y=RT, colour=factor(targSpeed), group=factor(targSpeed))) +  
    stat_smooth(method='lm', formula=y~ns(x,4)) + 
    labs(x='Mask Speed', y='RT',colour='Target Speed') + theme_black()
```

### Quintic effects
```{r, fig.height=3, fig.width=5}
ggplot(md, aes(x=maskSpeed, y=RT, colour=factor(targSpeed), group=factor(targSpeed))) +  
    stat_smooth(method='lm', formula=y~ns(x,5)) + 
    labs(x='Mask Speed', y='RT',colour='Target Speed') + theme_black()
```

## Simple model
Running a simple linear model reveals an effect of target speed, but not the mask speed or the interaction between mask and target speed. The main effect of mask speed does, however, approach significance.
```{r}
# Running the simplest model
m1 <- lmer(RT~maskSpeed*targSpeed+(1|SubjID), md)
anova(m1)
summary(m1)
2 * (1 - pnorm(abs(data.frame(coef(summary(m1)))$t.value))) # approx p's
```

## Nuisance variables
The above findings remain in place when the models including target and mask speeds (as well as their interaction) are compared against models containing only the nuisance variables (subject's individual threshold and the trial number).
```{r}
# Nuisance variable model with trial and subjThresh
mn <- lmer(RT~subjThresh+trial+(1|SubjID), md)
anova(mn)
summary(mn)
2 * (1 - pnorm(abs(data.frame(coef(summary(mn)))$t.value))) # approx p's
# Effects of mask speed and target speed:
mp_m <- lmer(RT~subjThresh+trial+maskSpeed+(1|SubjID), md)
mp_t <- lmer(RT~subjThresh+trial+targSpeed+(1|SubjID), md)
mp_mpt <- lmer(RT~subjThresh+trial+maskSpeed+targSpeed+(1|SubjID), md)
anova(mp_m,mp_mpt) # effect of target speed
anova(mp_t,mp_mpt) # effect of mask speed

# Effects of target and mask speed (testing interaction)
mp_mxt <- lmer(RT~subjThresh+trial+maskSpeed*targSpeed+(1|SubjID), md)
anova(mp_mpt,mp_mxt)
summary(mp_mxt)
2 * (1 - pnorm(abs(data.frame(coef(summary(mp_mxt)))$t.value))) # approx p's

# Full model
mp_full <- lmer(RT~trial+subjThresh*maskSpeed*targSpeed+(1|SubjID), md)
anova(mp_mxt,mp_full)
summary(mp_full)
( pvalfn(mp_full) )

library('ez')
ezANOVA(md[!is.na(md$RT),], dv=RT, wid=SubjID, within=.(targSpeed, maskSpeed),
        between_covariates=subjThresh)
```

## Testing the two target speeds in separate models
```{r}
# Low target speeds
md1 <- md[md$targSpeed==1,]
m1md1 <- lmer(RT~maskSpeed+(1|SubjID), md1)
anova(m1md1)
summary(m1md1)
2 * (1 - pnorm(abs(data.frame(coef(summary(m1md1)))$t.value))) # approx p's

# High target speeds
md2 <- md[md$targSpeed==5,]
m1md2 <- lmer(RT~maskSpeed+(1|SubjID), md2)
anova(m1md2)
summary(m1md2)
2 * (1 - pnorm(abs(data.frame(coef(summary(m1md2)))$t.value))) # approx p's
```

## Non-linear (quadratic and cubic) trends
```{r}
# Low target speed
fitLin <- lm(RT~maskSpeed, data=md1)
fitSquare <- nls(RT~a+b*maskSpeed^2, data=md1, start=list(a=1,b=0))
summary(fitSquare)
anova(fitLin, fitSquare)
fitCube <- nls(RT~a+b*maskSpeed^3, data=md1, start=list(a=1,b=0))
summary(fitCube)
anova(fitSquare, fitCube)
fitQuatric <- nls(RT~a+b*maskSpeed^4, data=md1, start=list(a=1,b=0))
summary(fitQuatric )
anova(fitCube, fitQuatric )

# High target speed
fitLin <- lm(RT~maskSpeed, data=md2)
fitSquare <- nls(RT~a+b*maskSpeed^2, data=md2, start=list(a=1,b=0))
summary(fitSquare)
anova(fitLin, fitSquare)
fitCube <- nls(RT~a+b*maskSpeed^3, data=md2, start=list(a=1,b=0))
summary(fitCube)
anova(fitLin, fitCube)
fitQuatric <- nls(RT~a+b*maskSpeed^4, data=md2, start=list(a=1,b=0))
summary(fitQuatric )
anova(fitLin, fitQuatric )

### to compute better starting values for convergence:
# f <- function(x,a,b) {a * exp(b * x)}
# st <- coef(nls(log(RT) ~ log(f(maskSpeed, a, b)), md1, start = c(a=1, b=1)))
# summary(nls(RT ~ f(maskSpeed, a, b), md1, start = st))
```

### Normalized data set
```{r}
# Compiling a data set containing two normalized values
# Normalizing by subject
mds <- ddply(md, .(SubjID), summarise, subjMean=mean(RT, na.rm=T))
mdn <- merge(md,mds,by='SubjID')
# Normalizing by motion pattern
mdc <- ddply(md, .(SubjID, targSpeed), summarise, condMean=mean(RT, na.rm=T))
mdn <- merge(mdn,mdc,by=c('SubjID','targSpeed'))
# Computing the normalized RTs
mdn$subjNormRT <- mdn$RT / mdn$subjMean
ddply(mdn,.(maskSpeed, targSpeed), summarise, stdev=sd(subjNormRT,na.rm=T))
# Computing the subject means for dot-plotting:
subjMeans <- ddply(mdn, .(SubjID, targSpeed, maskSpeed), summarise, subjMean=mean(subjNormRT, na.rm=T))
```

### Quartic effects
```{r, fig.height=4, fig.width=7}
# pdf("expt4b2-4.pdf", width=7, height=4)
# ggplot(mdn, aes(x=maskSpeed, y=subjNormRT, colour=factor(targSpeed))) + #, group=targSpeed)) +  
#     # stat_smooth(method='loess', alpha=.1, aes(fill=factor(targSpeed)), show_guide=F, se=T, na.rm=T) + 
#     stat_smooth(method='lm', formula=y~ns(x,4), alpha=.1, aes(fill=factor(targSpeed)), show_guide=F, se=T, na.rm=T) +
#     geom_point(data=subjMeans, aes(x=maskSpeed, y=subjMean, colour=factor(targSpeed)), 
#                position=position_dodge(width=.25), size=.7, alpha=.5) + # square is shape=7
#     labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), 
#          y='Normalized RT', colour='Target Speed\n') + 
#     scale_x_continuous(breaks=unique(mdn$maskSpeed)) + 
#     scale_colour_manual( breaks=c(1,5), labels=c(
#             expression(paste(' 1 ', degree, '/s', sep='')),
#             expression(paste(' 5 ', degree, '/s', sep=''))),
#         values=c('#E69F00', '#0072B2')) + theme_black()
# dev.off()
# pdf("expt4bw-3.pdf", width=5, height=3)
# ggplot(mdn, aes(x=maskSpeed, y=subjNormRT, colour=factor(targSpeed))) + #, group=targSpeed)) +  
#     stat_smooth(method='lm', formula=y~ns(x,3), alpha=.1, aes(fill=factor(targSpeed)), show_guide=F, 
#                 se=T, na.rm=T) + 
#     geom_point(data=subjMeans, aes(x=maskSpeed, y=subjMean, colour=factor(targSpeed)), 
#                position=position_dodge(width=.25), size=.7, alpha=.5) + # square is shape=7
#     labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), 
#          y='Normalized RT', colour='Target Speed\n') + 
#     scale_x_continuous(breaks=unique(mdn$maskSpeed)) + 
#     scale_colour_manual( breaks=c(1,5), labels=c(
#             expression(paste(' 1 ', degree, '/s', sep='')),
#             expression(paste(' 5 ', degree, '/s', sep=''))),
#         values=c('#E69F00', '#0072B2')) + 
#     theme_bw()
# dev.off()
# pdf("expt4bw-2.pdf", width=5, height=3)
# ggplot(mdn, aes(x=maskSpeed, y=subjNormRT, colour=factor(targSpeed))) + #, group=targSpeed)) +  
#     stat_smooth(method='lm', formula=y~ns(x,2), alpha=.1, aes(fill=factor(targSpeed)), show_guide=F, 
#                 se=T, na.rm=T) + 
#     geom_point(data=subjMeans, aes(x=maskSpeed, y=subjMean, colour=factor(targSpeed)), 
#                position=position_dodge(width=.25), size=.7, alpha=.5) + # square is shape=7
#     labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), 
#          y='Normalized RT', colour='Target Speed\n') + 
#     scale_x_continuous(breaks=unique(mdn$maskSpeed)) + 
#     scale_colour_manual( breaks=c(1,5), labels=c(
#             expression(paste(' 1 ', degree, '/s', sep='')),
#             expression(paste(' 5 ', degree, '/s', sep=''))),
#         values=c('#E69F00', '#0072B2')) + 
#     theme_bw()
# dev.off()
pdf("expt4bw-4.pdf", width=5, height=3)
ggplot(mdn, aes(x=maskSpeed, y=subjNormRT, colour=factor(targSpeed))) + #, group=targSpeed)) +  
    # stat_smooth(method='loess', alpha=.1, aes(fill=factor(targSpeed)), show_guide=F, se=T, na.rm=T) + 
    stat_smooth(method='lm', formula=y~ns(x,4), alpha=.1, aes(fill=factor(targSpeed)), show_guide=F, se=T, na.rm=T) + 
    geom_point(data=subjMeans, aes(x=maskSpeed, y=subjMean, colour=factor(targSpeed)), 
               position=position_dodge(width=.25), size=.7, alpha=.5) + # square is shape=7
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), 
         y='Normalized RT', colour='Target Speed\n') + 
    scale_x_continuous(breaks=unique(mdn$maskSpeed)) + 
    scale_colour_manual( breaks=c(1,5), labels=c(
            expression(paste(' 1 ', degree, '/s', sep='')),
            expression(paste(' 5 ', degree, '/s', sep=''))),
        values=c('#E69F00', '#0072B2')) + theme_bw()
dev.off()
pdf("expt4bw2-3.pdf", width=5, height=3)
ggplot(subjMeans, aes(x=maskSpeed, y=subjMean, colour=factor(targSpeed))) + #, group=targSpeed)) +  
    # stat_smooth(method='loess', alpha=.1, aes(fill=factor(targSpeed)), show_guide=F, se=T, na.rm=T) + 
    stat_smooth(method='lm', formula=y~ns(x,3), alpha=.1, aes(fill=factor(targSpeed)), show_guide=F, se=T, na.rm=T) + 
    geom_point(data=subjMeans, aes(x=maskSpeed, y=subjMean, colour=factor(targSpeed)), 
               position=position_dodge(width=.25), size=.7, alpha=.5) + # square is shape=7
    labs(x=expression(paste('Mask Speed (', degree, '/s)', sep='')), 
         y='Normalized RT', colour='Target Speed\n') + 
    scale_x_continuous(breaks=unique(mdn$maskSpeed)) + 
    scale_colour_manual( breaks=c(1,5), labels=c(
            expression(paste(' 1 ', degree, '/s', sep='')),
            expression(paste(' 5 ', degree, '/s', sep=''))),
        values=c('#E69F00', '#0072B2')) + theme_bw()
dev.off()
```